\section{Polynomials}

\setcounter{subsection}{1}

\begin{exercise}[4a1]
    Suppose $w, z \in \c$. Verify the following equalities and inequalities.
    \begin{subexercises}
        \item $z + \bar{z} = 2 \Re z$
        \item $z - \bar{z} = 2(\Im z)i$
        \item $z\bar{z} = |z|^2$
        \item $\bar{w + z} = \bar{w} + \bar{z}$ and $\bar{wz} = \bar{w} \bar{z}$
        \item $\bar{\bar{z}} = z$
        \item $|\Re z| \leq |z|$ and $|\Im z| \leq |z|$
        \item $|\bar{z}| = |z|$
        \item $|wz| = |w| |z|$
    \end{subexercises}
\end{exercise}

\begin{sol}
    In this problem, let $z = a + bi$ and $w = c + di$ with $a, b, c, d \in \r$. Then
    \begin{subexercises}
        \item $z + \bar{z} = (a + bi) + (a - bi) = 2a = 2 \Re z$.
        \item $z - \bar{z} = (a + bi) - (a - bi) = 2bi = 2(\Im z)i$.
        \item $z\bar{z} = (a + bi)(a - bi) = a^2 + b^2 = |z|^2$.
        \item $\bar{w + z} = \bar{(c + di) + (a + bi)} = \bar{(a + c) + (b + d)i} = (a + c) - (b + d)i = (a - bi) + (c - di) = \bar{w} + \bar{z}$ and $\bar{wz} = \bar{(c + di)(a + bi)} = \bar{(ac - bd) + (ad + bc)i} = (ac - bd) - (ad + bc)i = (c - di)(a - bi) = \bar{w} \bar{z}$.
        \item $\bar{\bar{z}} = \bar{a - bi} = a + bi = z$.
        \item $|\Re z| = |a| \leq \sqrt{a^2 + b^2} = |z|$ and $|\Im z| = |b| \leq \sqrt{a^2 + b^2} = |z|$.
        \item $|\bar{z}| = |a - bi| = \sqrt{a^2 + b^2} = |z|$.
        \item $|wz| = |(c + di)(a + bi)| = |(ac - bd) + (ad + bc)i| = \sqrt{(ac - bd)^2 + (ad + bc)^2} = \sqrt{(a^2 + b^2)(c^2 + d^2)} = |a + bi| |c + di| = |z| |w|$. \qh
    \end{subexercises}
\end{sol}

\begin{exercise}[4a2]
    Prove that if $w, z \in \c$, then $||w| - |z|| \leq |w - z|$.
    
    \note{The inequality above is called the \emph{\textbf{reverse triangle inequality}}.}
\end{exercise}

\begin{sol}
    Let $w, z \in \c$. By the triangle inequality, we have
    \[|w| = |(w - z) + z| \leq |w - z| + |z|.\]
    Rearranging gives $|w| - |z| \leq |w - z|$. Similarly,
    \[|z| = |(z - w) + w| \leq |z - w| + |w| = |w - z| + |w|,\]
    which gives $|z| - |w| \leq |w - z|$, or equivalently $-|w - z| \leq |w| - |z|$. Combining these inequalities, we get
    \[||w| - |z|| \leq |w - z|. \qh\]
\end{sol}

\begin{exercise}[4a3]
    Suppose $V$ is a complex vector space and $\varphi \in V'$. Define $\sigma: V \to \r$ by $\sigma(v) = \Re \varphi(v)$ for each $v \in V$. Show that
    \[\varphi(v) = \sigma(v) - i\sigma(iv)\]
    for all $v \in V$.
\end{exercise}

\begin{sol}
    Let $v \in V$. Then there exist $s, t \in \r$ such that
    \[\varphi(v) = s + ti.\]
    Then
    \[\sigma(v) = \Re \varphi(v) = s \quad \text{and} \quad \sigma(iv) = \Re \varphi(iv) = \Re (i(s + ti)) = \Re (-t + si) = -t.\]
    Therefore,
    \[\sigma(v) - i\sigma(iv) = s - i(-t) = s + ti = \varphi(v). \qh\]
\end{sol}

\begin{exercise}[4a4]
    Suppose $m$ is a positive integer. Is the set
    \[\set{0} \cup \set{p \in \pp(\f) \mid \deg p = m}\]
    a subspace of $\pp(\f)$?
\end{exercise}

\begin{sol}
    No, the set is not a subspace of $\pp(\f)$. To see this, consider two polynomials $p, q \in \pp(\f)$ with $p(x) = x^m$ and $q(x) = -x^m + x^{m - 1}$. Then $p + q = x^{m - 1}$, which has degree $m - 1$ and is not in the set. Therefore, the set is not closed under addition and hence not a subspace.
\end{sol}

\begin{exercise}[4a5]
    Is the set
    \[\set{0} \cup \set{p \in \pp(\f) \mid \deg p \text{ is even}}\]
    a subspace of $\pp(\f)$?
\end{exercise}

\begin{sol}
    No, the set is not a subspace of $\pp(\f)$. To see this, consider two polynomials $p, q \in \pp(\f)$ with $p(x) = x^2$ and $q(x) = x - x^2$. Then $p + q = x$, which has degree $1$ and is not even. Therefore, the set is not closed under addition and hence not a subspace.
\end{sol}

\begin{exercise}[4a6]
    Suppose that $m$ and $n$ are positive integers with $m \leq n$, and suppose $\lambda_1, \ldots, \lambda_m \in \f$. Prove that there exists a polynomial $p \in \pp(\f)$ with $\deg p = n$ such that $0 = p(\lambda_1) = \cdots = p(\lambda_m)$ and such that $p$ has no other zeros.
\end{exercise}

\begin{sol}
    Consider the polynomial
    \[p(x) = (x - \lambda_1)^{n - m + 1}(x - \lambda_2) \cdots (x - \lambda_m).\]
    This polynomial has degree $n$, vanishes at $\lambda_1, \ldots, \lambda_m$, and has no other zeros. Therefore, it satisfies the required conditions.
\end{sol}

\begin{exercise}[4a7]
    Suppose that $m$ is a nonnegative integer, $z_1, \ldots, z_{m + 1}$ are distinct elements of $\f$, and $w_1, \ldots, w_{m + 1} \in \f$. Prove that there exists a unique polynomial $p \in \pp_m(\f)$ such that
    \[p(z_k) = w_k\]
    for each $k = 1, \ldots, m + 1$.
    
    \note{This result can be proved without using linear algebra. However, try to find the clearer, shorter proof that uses some linear algebra.}
\end{exercise}

\begin{sol}
    Consider the linear map $T: \pp_m(\f) \to \f^{m + 1}$ defined by
    \[T(p) = (p(z_1), \ldots, p(z_{m + 1})).\]
    Since $\dim \pp_m(\f) = m + 1$ and $\dim \f^{m + 1} = m + 1$, it suffices to show that $T$ is injective to conclude that it is also surjective. Suppose $T(p) = 0$, i.e., $p(z_k) = 0$ for all $k = 1, \ldots, m + 1$. Since $p$ has degree at most $m$ and has $m + 1$ distinct zeros, it must be the zero polynomial. Therefore, $T$ is injective, and hence bijective. This shows that for any $(w_1, \ldots, w_{m + 1}) \in \f^{m + 1}$, there exists a unique $p \in \pp_m(\f)$ such that $T(p) = (w_1, \ldots, w_{m + 1})$, which is exactly the desired polynomial.
\end{sol}

\begin{exercise}[4a8]
    Suppose $p \in \pp(\c)$ has degree $m$. Prove that $p$ has $m$ distinct zeros if and only if $p$ and its derivative $p'$ have no zeros in common.
\end{exercise}

\begin{sol}
    Suppose $p$ has $m$ distinct zeros, say $z_1, \ldots, z_m$. If $p$ and $p'$ have a common zero $z_k$, then $z_k$ would be a multiple zero of $p$, contradicting the assumption that all zeros are distinct. Hence, $p$ and $p'$ have no zeros in common.

    Conversely, suppose $p$ and $p'$ have no zeros in common. If $p$ had a multiple zero $z$, then $p(z) = 0$ and $p'(z) = 0$, which would contradict the assumption. Therefore, all zeros of $p$ are distinct.
\end{sol}

\begin{exercise}[4a9]
    Prove that every polynomial of odd degree with real coefficients has a real zero.
\end{exercise}

\begin{sol}
    Let $p(x)$ be a polynomial of odd degree with real coefficients. As $x \to \infty$, $p(x) \to \infty$ or $p(x) \to -\infty$ depending on the leading coefficient. Similarly, as $x \to -\infty$, $p(x) \to -\infty$ or $p(x) \to \infty$. By the intermediate value theorem, since $p(x)$ is continuous and takes on both positive and negative values, there must exist some $x \in \r$ such that $p(x) = 0$. Therefore, $p$ has a real zero.
\end{sol}

\begin{exercise}[4a10]
    For $p \in \pp(\r)$, define $Tp: \r \to \r$ by
    \[(Tp)(x) = \begin{cases}
        \frac{p(x) - p(3)}{x - 3} & \text{if } x \neq 3, \\
        p'(3) & \text{if } x = 3
    \end{cases}\]
    for each $x \in \r$. Show that $Tp \in \pp(\r)$ for every polynomial $p \in \pp(\r)$ and also show that $T: \pp(\r) \to \pp(\r)$ is a linear map.
\end{exercise}

\begin{sol}
    Let $p(x) = a_0 + a_1 x + \cdots + a_n x^n$. For $x \neq 3$, we have
    \[(Tp)(x) = \frac{p(x) - p(3)}{x - 3} = \frac{1}{x - 3} \sum_{k = 0}^n a_k (x^k - 3^k).\]
    We claim that
    \[x^k - 3^k = (x - 3)(x^{k-1} + x^{k-2} \cdot 3 + \cdots + x \cdot 3^{k-2} + 3^{k-1}).\]
    By induction, we check the base case $k = 1$. Since $x^1 - 3^1 = x - 3$, the formula holds for $k = 1$. Assuming it holds for some $k$, then for $k + 1$, we have
    \begin{align*}
        x^{k+1} - 3^{k+1} &= x \cdot x^k - 3 \cdot 3^k \\
        &= x(x^k - 3^k) + 3^k (x - 3) \\
        &= x(x - 3)(x^{k-1} + x^{k-2} \cdot 3 + \cdots + x \cdot 3^{k-2} + 3^{k-1}) + 3^k (x - 3) \\
        &= (x - 3)(x(x^{k-1} + x^{k-2} \cdot 3 + \cdots + x \cdot 3^{k-2} + 3^{k-1}) + 3^k) \\
        &= (x - 3)(x^k + x^{k-1} \cdot 3 + \cdots + x \cdot 3^{k-1} + 3^k),
    \end{align*}
    which completes the induction step. Therefore, when we divide by $x - 3$, we obtain a polynomial of degree $k - 1$, and hence $(Tp)(x)$ is a polynomial of degree $n - 1$. This shows that $Tp \in \pp(\r)$.

    Now let $p, q \in \pp(\r)$ and let $a, b \in \r$. If $x = 3$, then
    \[T(ap + bq)(3) = (ap + bq)'(3) = a p'(3) + b q'(3) = a Tp(3) + b Tq(3).\]
    If $x \neq 3$, then
    \[T(ap + bq)(x) = \frac{(ap + bq)(x) - (ap + bq)(3)}{x - 3} = \frac{a(p(x) - p(3)) + b(q(x) - q(3))}{x - 3} = a Tp(x) + b Tq(x).\]
    Hence, $T(ap + bq) = a Tp + b Tq$, which shows that $T$ is linear.
\end{sol}

\begin{exercise}[4a11]
    Suppose $p \in \pp(\c)$. Define $q: \c \to \c$ by
    \[q(z) = p(z) \bar{p(\bar{z})}.\]
    Prove that $q$ is a polynomial with real coefficients.
\end{exercise}

\begin{sol}
    Let $p \in \pp(\c)$ have degree $n$. Then we may write
    \[p(z) = \alpha(z - \lambda_1)(z - \lambda_2) \cdots (z - \lambda_n),\]
    where $\alpha \in \c$ and $\lambda_1, \lambda_2, \ldots, \lambda_n \in \c$ are the roots of $p$. Then
    \[q(z) = p(z) \bar{p(\bar{z})} = \alpha(z - \lambda_1)(z - \lambda_2) \cdots (z - \lambda_n) \cdot \bar{\alpha} (z - \bar{\lambda_1}) (z - \bar{\lambda_2}) \cdots (z - \bar{\lambda_n}).\]
    Note that the product contains the term $\alpha\bar\alpha = |\alpha|^2 \in \r$, as well as the pairs
    \[(z - \lambda_i)(z - \bar{\lambda_i}) = z^2 - 2\Re(\lambda_i) z + |\lambda_i|^2.\]
    Each such pair contributes a quadratic polynomial with real coefficients. Since the product of polynomials with real coefficients also has real coefficients, it follows that $q(z)$ is a polynomial with real coefficients.
\end{sol}

\begin{exercise}[4a12]
    Suppose $m$ is a nonnegative integer and $p \in \pp_m(\c)$ is such that there are distinct real numbers $x_0, x_1, \ldots, x_m$ with $p(x_k) \in \r$ for each $k = 0, 1, \ldots, m$. Prove that all coefficients of $p$ are real.
\end{exercise}

\begin{sol}
    Let $p(x_k) = y_k \in \r$ for each $k = 0, 1, \ldots, m$. By \autoref{ex:4a7} with $\f = \r$, there exists a polynomial $q \in \pp_m(\r)$ that satisfies $q(x_k) = y_k$ for each $k = 0, 1, \ldots, m$. Note that this polynomial must be the same as the original $p \in \pp_m(\c)$ because a polynomial of degree at most $m$ is uniquely determined by its values at $m+1$ distinct points. Therefore, all coefficients of $p$ are real.
\end{sol}

\begin{exercise}[4a13]
    Suppose $p \in \pp(\f)$ with $p \neq 0$. Let $U = \set{pq \mid q \in \pp(\f)}$.
    \begin{subexercises}
        \item Show that $\dim \pp(\f) / U = \deg p$.
        \item Find a basis of $\pp(\f) / U$.
    \end{subexercises}
\end{exercise}

\begin{sole}
    \item We first show that $U$ is a subspace of $\pp(\f)$. Clearly, $0 \in U$ since $0 = p \cdot 0$. If $u_1, u_2 \in U$, then $u_1 = pq_1$ and $u_2 = pq_2$ for some $q_1, q_2 \in \pp(\f)$. For any scalars $\alpha, \beta \in \f$, we have $\alpha u_1 + \beta u_2 = \alpha pq_1 + \beta pq_2 = p(\alpha q_1 + \beta q_2) \in U$. Therefore, $U$ is closed under addition and scalar multiplication, and hence $U$ is a subspace of $\pp(\f)$.
    
    Now let $r \in \pp(\f)$. By the division algorithm for polynomials, there exist unique polynomials $q_0 \in \pp(\f)$ and $s \in \pp(\f)$ with $\deg s < \deg p$ such that $r = pq_0 + s$. This shows that every polynomial in $\pp(\f)$ can be written as an element of $U$ plus a polynomial of degree less than $\deg p$. Consider the map $T : \pp_{\deg p - 1}(\f) \to \pp(\f) / U$ defined by $T(s) = s + U$. This map is linear and surjective, and its kernel is trivial since if $s + U = U$, then $s \in U$, which implies $s = pq$ for some $q \in \pp(\f)$. But $\deg s < \deg p$, so $s$ must be zero. Therefore, $T$ is an isomorphism, and we conclude that $\dim \pp(\f) / U = \dim \pp_{\deg p - 1}(\f) = \deg p$.
    \item A basis of $\pp(\f) / U$ is given by the images of the standard basis of $\pp_{\deg p - 1}(\f)$ under $T$, namely $\set{1 + U, x + U, \ldots, x^{\deg p - 1} + U}$.
\end{sole}

\begin{exercise}[4a14]
    Suppose $p, q \in \pp(\c)$ are nonconstant polynomials with no zeros in common. Let $m = \deg p$ and $n = \deg q$. Use linear algebra as outlined below in (a)--(c) to prove that there exist $r \in \pp_{n-1}(\c)$ and $s \in \pp_{m-1}(\c)$ such that
    \[rp + sq = 1.\]
    \begin{subexercises}
        \item Define $T: \pp_{n-1}(\c) \times \pp_{m-1}(\c) \to \pp_{m+n-1}(\c)$ by
        \[T(r, s) = rp + sq.\]
        Show that the linear map $T$ is injective.
        \item Show that the linear map $T$ in (a) is surjective.
        \item Use (b) to conclude that there exist $r \in \pp_{n-1}(\c)$ and $s \in \pp_{m-1}(\c)$ such that $rp + sq = 1$.
    \end{subexercises}
\end{exercise}

\begin{sole}
    \item To show that $T$ is injective, suppose that $T(r, s) = rp + sq = 0$ for some $(r, s) \in \pp_{n-1}(\c) \times \pp_{m-1}(\c)$. Then $rp = -sq$ so that $q$ divides $rp$. Since $p$ and $q$ have no zeros in common, $q$ must divide $r$. But $\deg r < \deg q$, so the only possibility is that $r = 0$. Then $-sq = 0$. Since $q$ is nonconstant, this implies that $s = 0$. Therefore, the kernel of $T$ is trivial, and $T$ is injective.
    \item To show that $T$ is surjective, note that $\dim(\pp_{n-1}(\c) \times \pp_{m-1}(\c)) = n + m = \dim \pp_{m+n-1}(\c)$. Since $T$ is a linear map between vector spaces of the same finite dimension, and we have already shown that $T$ is injective, it follows that $T$ is also surjective.
    \item The existence of such polynomials $r$ and $s$ demonstrates that $1$ lies in the image of $T$, which is precisely what we wanted to prove: there exist $r \in \pp_{n-1}(\c)$ and $s \in \pp_{m-1}(\c)$ such that $rp + sq = 1$.
\end{sole}