\subsection{Invertibility and Isomorphisms}

\begin{exercise}[3d1]
    Suppose $T \in \lin{V, W}$ is invertible. Show that $T\inv$ is invertible and
    \[(T\inv)\inv = T.\]
\end{exercise}

\begin{sol}
    Since $T$ is invertible, then $T\inv \in \lin{W, V}$. By $TT\inv = I$ and $T\inv T = I$, we have that $T\inv$ is invertible and $(T\inv)\inv = T$.
\end{sol}

\begin{exercise}[3d2]
    Suppose $T \in \lin{U, V}$ and $S \in \lin{V, W}$ are both invertible linear maps. Prove that $ST \in \lin{U, W}$ is invertible and that $(ST)\inv = T\inv S\inv$.
\end{exercise}

\begin{sol}
    Since $T$ and $S$ are invertible, then $T\inv \in \lin{V, U}$ and $S\inv \in \lin{W, V}$. By the definition of the inverse, we have that
    \[(ST)(T\inv S\inv) = S(TT\inv)S\inv = SIS\inv = SS\inv = I,\]
    and
    \[(T\inv S\inv)(ST) = T\inv(S\inv S)T = T\inv IT = T\inv T = I.\]
    Thus, $ST$ is invertible and $(ST)\inv = T\inv S\inv$.
\end{sol}

\begin{exercise}[3d3]
    Suppose $V$ is finite-dimensional and $T \in \lin{V}$. Prove that the following are equivalent.
    \begin{subexercises}
        \item $T$ is invertible.
        \item $Tv_1, \ldots, Tv_n$ is a basis of $V$ for every basis $v_1, \ldots, v_n$ of $V$.
        \item $Tv_1, \ldots, Tv_n$ is a basis of $V$ for some basis $v_1, \ldots, v_n$ of $V$.
    \end{subexercises}
\end{exercise}

\begin{solitem}
    \item (a) $\implies$ (b): Suppose $T$ is invertible. Then $T\inv \in \lin{V}$. Let $v_1, \ldots, v_n$ be a basis of $V$. Since $T\inv$ is invertible, then $T\inv v_1, \ldots, T\inv v_n$ is a basis of $V$. Then there exist scalars $\alpha_1, \ldots, \alpha_n$ such that
    \[v = \alpha_1 T\inv v_1 + \cdots + \alpha_n T\inv v_n\]
    for every $v \in V$. Applying $T$ to both sides, we have
    \[Tv = \alpha_1 v_1 + \cdots + \alpha_n v_n\]
    for every $v \in V$. Thus, $Tv_1, \ldots, Tv_n$ spans $V$. Now suppose that
    \[\alpha_1 Tv_1 + \cdots + \alpha_n Tv_n = 0\]
    for some scalars $\alpha_1, \ldots, \alpha_n$. Applying $T\inv$ to both sides, we have
    \[\alpha_1 v_1 + \cdots + \alpha_n v_n = 0.\]
    Since $v_1, \ldots, v_n$ is a basis of $V$, then $\alpha_1 = \cdots = \alpha_n = 0$. Hence, $Tv_1, \ldots, Tv_n$ is linearly independent. Since $Tv_1, \ldots, Tv_n$ spans $V$ and is linearly independent, then $Tv_1, \ldots, Tv_n$ is a basis of $V$.
    \item (b) $\implies$ (c): This is trivial.
    \item (c) $\implies$ (a): Suppose $Tv_1, \ldots, Tv_n$ is a basis of $V$ for some basis $v_1, \ldots, v_n$ of $V$. Then $\range T = V$. By the rank-nullity theorem, we have that $\dim \nul T = 0$. Thus, $T$ is injective. Since $T$ is injective and $\range T = V$, then $T$ is invertible.
\end{solitem}

\begin{exercise}[3d4]
    Suppose $V$ is finite-dimensional and $\dim V > 1$. Prove that the set of non-invertible linear maps from $V$ to itself is not a subspace of $\lin{V}$.
\end{exercise}

\begin{sol}
    Let $v_1, \ldots, v_n$ be a basis of $V$. Define $T, S \in \lin V$ such that
    \[Tv_1 = 0, \quad Tv_k = v_k \text{ for } k = 2, \ldots, n,\]
    and
    \[Sv_1 = v_1, \quad Sv_k = 0 \text{ for } k = 2, \ldots, n.\]
    Then $T$ and $S$ are non-invertible linear maps, since $\nul T = \spn v_1$ and $\nul S = \spn(v_2, \ldots, v_n)$. However, $T + S$ is invertible, since
    \[(T + S)v_1 = v_1, \quad (T + S)v_k = v_k \text{ for } k = 2, \ldots, n.\]
    Hence, $T + S = I$ is invertible. Therefore, the set of non-invertible linear maps from $V$ to itself is not a subspace of $\lin{V}$.
\end{sol}

\begin{exercise}[3d5]
    Suppose $V$ is finite-dimensional, $U$ is a subspace of $V$, and $S \in \lin{U, V}$. Prove that there exists an invertible linear map $T$ from $V$ to itself such that $Tu = Su$ for every $u \in U$ if and only if $S$ is injective.
\end{exercise}

\begin{sol}
    Suppose there exists an invertible linear map $T$ from $V$ to itself such that $Tu = Su$ for every $u \in U$. If $Su = 0$, then $Tu = 0$, and since $T$ is invertible, $u = 0$. Hence, $S$ is injective.

    Conversely, suppose $S$ is injective. Let $u_1, \ldots, u_m$ be a basis of $U$. Since $S$ is injective, then $Su_1, \ldots, Su_m$ is linearly independent. Extend $u_1, \ldots, u_m$ to a basis $u_1, \ldots, u_n$ of $V$. Extend $Su_1, \ldots, Su_m$ to a basis $v_1, \ldots, v_n$ of $V$. Define $T \in \lin{V}$ such that
    \[Tu_k = Su_k \text{ for } k = 1, \ldots, m, \quad Tu_k = v_k \text{ for } k = m + 1, \ldots, n.\]
    Then $T$ is invertible, since $Tu_1, \ldots, Tu_n$ is a basis of $V$. Thus, there exists an invertible linear map $T$ from $V$ to itself such that $Tu = Su$ for every $u \in U$.
\end{sol}

\begin{exercise}[3d6]
    Suppose that $W$ is finite-dimensional and $S, T \in \lin{V, W}$. Prove that $\nul S = \nul T$ if and only if there exists an invertible $E \in \lin{W}$ such that $S = ET$.
\end{exercise}

\begin{sol}
    Suppose $\nul S = \nul T$. Then $\dim \range S = \dim \range T$. Define a linear map $E$ from $\range T$ to $\range S$ by setting $E(Tv) = Sv$ for all $v \in V$. This is well-defined because if $Tv = Tv'$ for some $v, v' \in V$, then $T(v - v') = 0$, so $v - v' \in \nul T = \nul S$, and thus $S(v - v') = 0$, which implies $Sv = Sv'$. Extend $E$ to an invertible linear map on $W$. Then $S = ET$.

    Conversely, suppose there exists an invertible $E \in \lin{W}$ such that $S = ET$. If $v \in \nul S$, then $Sv = 0$, and since $S = ET$, we have $ETv = 0$. Since $E$ is invertible, then $Tv = 0$, and thus $v \in \nul T$. Hence, $\nul S \subseteq \nul T$. Similarly, if $v \in \nul T$, then $Tv = 0$, and since $S = ET$, we have $Sv = ETv = E0 = 0$. Thus, $v \in \nul S$, and $\nul T \subseteq \nul S$. Therefore, $\nul S = \nul T$.
\end{sol}

\begin{exercise}[3d7]
    Suppose that $V$ is finite-dimensional and $S, T \in \lin{V, W}$. Prove that $\range S = \range T$ if and only if there exists an invertible $E \in \lin{V}$ such that $S = TE$.
\end{exercise}

\begin{sol}
    Suppose $\range S = \range T$. Then $\dim \nul S = \dim \nul T$. Let $u_1, \ldots, u_k$ be a basis of $\nul S$ and $v_1, \ldots, v_k$ be a basis of $\nul T$. Extend both bases to a basis of $V$, say $u_1 \ldots, u_n$ and $v_1, \ldots, v_n$. Observe that for $i > k$, we have that $Su_i \in \range S = \range T$. Then there must exist $y_i \in V$ such that $Ty_i = Su_i$. Define a linear map $E \in \lin{V}$ by setting $Eu_i = v_i$ for $i \leq k$ and $Eu_i = y_i$ for $i > k$. To see that $TE = S$, we have for $i \leq k$ that $TEu_i = Tv_i = 0 = Su_i$. Moreover, for $i > k$, we have $TEu_i = Ty_i = Su_i$. To see that $E$ is invertible, suppose we have scalars $\alpha_1, \ldots, \alpha_n$ such that
    \[\alpha_1 Eu_1 + \alpha_2 Eu_2 + \cdots + \alpha_n Eu_n = 0.\]
    Applying $T$, we get
    \[\alpha_{k + 1} Su_{k + 1} + \cdots + \alpha_n Su_n = 0,\]
    where we used the fact that $TE = S$ and $Su_1 = \cdots = Su_k = 0$ because $u_1, \ldots, u_k \in \nul S$. Since $Su_{k + 1}, \ldots, Su_n$ are linearly independent (they form a basis of $\range S$), we must have $\alpha_{k + 1} = \cdots = \alpha_n = 0$. Then from the previous equation, $\alpha_1 v_1 + \cdots + \alpha_k v_k = 0$, and since $v_1, \ldots, v_k$ are linearly independent, we must have $\alpha_1 = \cdots = \alpha_k = 0$. Hence, all the scalars are zero, proving that $E$ is invertible.

    Conversely, suppose there exists an invertible $E \in \lin{V}$ such that $S = TE$. If $w \in \range S$, then there exists some $v \in V$ such that $Sv = w$. Since $S = TE$, we have $TEv = w$, and thus $w \in \range T$. Hence, $\range S \subseteq \range T$. Similarly, if $w \in \range T$, then there exists some $v \in V$ such that $Tv = w$. Since $E$ is invertible, there exists some $u \in V$ such that $Eu = v$. Then we have
    \[Su = TEu = Tv = w,\]
    and thus $w \in \range S$. Hence, $\range T \subseteq \range S$. Therefore, $\range S = \range T$.
\end{sol}

\begin{exercise}[3d8]
    Suppose $V$ and $W$ are finite-dimensional and $S, T \in \lin{V, W}$. Prove that there exist invertible $E_1 \in \lin{V}$ and $E_2 \in \lin{W}$ such that $S = E_2 T E_1$ if and only if $\dim \nul S = \dim \nul T$.
\end{exercise}

\begin{sol}
    Suppose there exist invertible $E_1 \in \lin{V}$ and invertible $E_2 \in \lin{W}$ such that $S = E_2 T E_1$. We claim that $E_1$ is an invertible map from $\nul S$ to $\nul T$. To see this, suppose $v, w \in \nul S$ and $E_1 v = E_1 w$. Then $v = w$ since $E_1$ is invertible, proving injectivity. To see surjectivity, let $u \in \nul T$. Since $E_1$ is invertible, there exists some $v \in V$ such that $E_1 v = u$. Then
    \[Sv = E_2 T E_1 v = E_2 T u = E_2 0 = 0,\]
    and thus $v \in \nul S$. Hence, $E_1$ is an invertible map from $\nul S$ to $\nul T$, and thus $\dim \nul S = \dim \nul T$.

    Conversely, suppose $\dim \nul S = \dim \nul T$. Then we may construct an invertible linear map $E_1 \in \lin{V}$ that maps $\nul S$ onto $\nul T$. We now claim that $\nul TE_1 = \nul S$. To see this, let $v \in \nul TE_1$. This is only true when $TE_1v = 0$, or $E_1v \in \nul T$. By invertibility of $E_1$, we have $v \in \nul S$. By \autoref{ex:3d6} with $\nul S = \nul TE_1$, there exists an invertible $E_2 \in \lin{W}$ such that $S = E_2 TE_1$.
\end{sol}

\begin{exercise}[3d9]
    Suppose $V$ is finite-dimensional and $T: V \to W$ is a surjective linear map of $V$ onto $W$. Prove that there is a subspace $U$ of $V$ such that $T|_U$ is an isomorphism of $U$ onto $W$.
    
    \note{Here $T|_U$ means the function $T$ restricted to $U$. Thus $T|_U$ is the function whose domain is $U$, with $T|_U(u) = Tu$ for every $u \in U$.}
\end{exercise}

\begin{sol}
    Since $T$ is surjective, then $\range T = W$. By \autoref{ex:3b11}, there exists a subspace $U$ of $V$ such that $V = \nul T \oplus U$. We show that $T|_U$ is an isomorphism of $U$ onto $W$. 

    Suppose $u \in U$ such that $T|_Uu = 0$. Then $Tu = 0$, and thus $u \in \nul T \cap U$. Since $V = \nul T \oplus U$, we have $\nul T \cap U = \{0\}$, and thus $u = 0$. This shows that $T|_U$ is injective.

    To see surjectivity, let $w \in W$. Since $T$ is surjective, there exists $v \in V$ such that $Tv = w$. Write $v = n + u$ with $n \in \nul T$ and $u \in U$. Then $Tu = T(v - n) = Tv - Tn = w - 0 = w$. Hence, $T|_U$ is surjective onto $W$, and therefore an isomorphism of $U$ onto $W$.
\end{sol}

\begin{exercise}[3d10]
    Suppose $V$ and $W$ are finite-dimensional and $U$ is a subspace of $V$. Let
    \[\ee = \set{T \in \lin{V, W} \mid U \subseteq \nul T}.\]
    \begin{subexercises}
        \item Show that $\ee$ is a subspace of $\lin{V, W}$.
        \item Find a formula for $\dim \ee$ in terms of $\dim V$, $\dim W$, and $\dim U$.
    \end{subexercises}
    \hint{Define $\Phi: \lin{V, W} \to \lin{U, W}$ by $\Phi(T) = T|_U$. What is $\nul \Phi$? What is $\range \Phi$?}
\end{exercise}

\begin{sole}
    \item Consider the zero map $0 \in \lin{V, W}$. For this map, $U \subseteq \nul 0$ since $\nul 0 = V$. Hence, $0 \in \ee$, showing that $\ee$ is non-empty. To see that $\ee$ is closed under addition and scalar multiplication, let $S, T \in \ee$ and $\alpha \in \f$. For any $u \in U$, we have $(S + T)u = Su + Tu = 0 + 0 = 0$, so $S + T \in \ee$. Similarly, $(\alpha T)u = \alpha (Tu) = \alpha \cdot 0 = 0$, so $\alpha T \in \ee$. Therefore, $\ee$ is a subspace of $\lin{V, W}$.
    \item Consider the linear map $\Phi: \lin{V, W} \to \lin{U, W}$ defined by $\Phi(T) = T|_U$. Let $T \in \lin{V, W}$ such that $\Phi(T) = T|_U = 0$. Then $T|_U = 0$ implies that for every $u \in U$, we have $Tu = 0$, i.e., $U \subseteq \nul T$. Hence, $T \in \ee$, showing that $\nul \Phi \subseteq \ee$. Conversely, if $T \in \ee$, then $U \subseteq \nul T$, which means that $T|_U = 0$, i.e., $T \in \nul \Phi$. Therefore, $\nul \Phi = \ee$, and $\dim \ee = \dim \nul \Phi$.
    
    We now show that $\Phi$ is surjective. Let $S \in \lin{U, W}$, and let $u_1, \ldots, u_m $ be a basis for $U$. Extend this to a basis $u_1, \ldots, u_m, v_1, \ldots, v_n$ for $V$. Define a linear map $T \in \lin{V, W}$ by setting $Tu_i = Su_i$ for $i = 1, \ldots, m$ and $Tv_j = 0$ for $j = 1, \ldots, n$. Then $T|_U = S$, so $\Phi(T) = S$. Hence, $\Phi$ is surjective, and $\range \Phi = \lin{U, W}$. Therefore, $\dim \range \Phi = \dim \lin{U, W} = (\dim U)(\dim W)$. By the rank-nullity theorem,
    \[\dim \lin{V, W} = \dim \nul \Phi + \dim \range \Phi = \dim \ee + (\dim U)(\dim W),\]
    Observing that $\dim \lin{V, W} = (\dim V)(\dim W)$, we get
    \[\dim \ee = (\dim V)(\dim W) - (\dim U)(\dim W) = (\dim V - \dim U)(\dim W). \qh\]
\end{sole}

\begin{exercise}[3d11]
    Suppose $V$ is finite-dimensional and $S, T \in \lin{V}$. Prove that
    \[ST \text{ is invertible} \iff S \text{ and } T \text{ are invertible}.\]
\end{exercise}

\begin{sol}
    Suppose $ST$ is invertible. Then it is injective. By \autoref{ex:3b19}, there exists $U \in \lin V$ such that $U(ST)$ is the identity operator. Since this is equal to $(US)T$, this implies that $T$ is injective. Since $T$ is injective on $\lin V$, it is also surjective, hence invertible.
    
    Note that $ST$ is also surjective. By \autoref{ex:3b20}, there exists $W \in \lin V$ such that $STW$ is the identity operator. Then $S(TW)$ implies that $S$ is surjective. Since it is surjective on $V$, then $S$ is also injective, hence invertible.

    Conversely, suppose $S$ and $T$ are invertible. This follows from \autoref{ex:3d2}.
\end{sol}

\begin{exercise}[3d12]
    Suppose $V$ is finite-dimensional and $S, T, U \in \lin{V}$ and $STU = I$. Show that $T$ is invertible and that $T\inv = US$.
\end{exercise}

\begin{sol}
    Since $STU = I$, then we have that $S(TU) = I$. By \autoref{ex:3b20}, then $S$ is surjective, hence injective. Then $S$ is invertible with $S\inv = TU$. Similarly, $(ST)U = I$. By \autoref{ex:3b19}, then $ST$ is injective, hence surjective. Then $ST$ is invertible with $(ST)\inv = U$. Then
    \[T(US) = (TU)S = S\inv S = I, \quad (US)T = U(ST) = (ST)\inv (ST) = I.\]
    Hence, $T$ is invertible with $T\inv = US$.
\end{sol}

\begin{exercise}[3d13]
    Show that the result in \autoref{ex:3d12} can fail without the hypothesis that $V$ is finite-dimensional.
\end{exercise}

\begin{sol}
    If $V$ were not finite-dimensional, let $v_1, v_2, \ldots$ be an infinite basis for $V$. Let $S, T, U \in \lin V$ be defined as follows: let $S = I$,
    \[Tv_1 = 0, \quad Tv_k = v_{k - 1}~\text{for}~k = 2, 3, \ldots\]
    and
    \[Uv_k = v_{k + 1}~\text{for}~k = 1, 2, \ldots\]
    It is clear that $TU v_k = v_k$ for all $k = 1, 2, \ldots$, so $STU = I$. However, $T$ is not injective since $\nul T = \spn v_1$, and thus $T$ is not invertible.
\end{sol}

\begin{exercise}[3d14]
    Prove or give a counterexample: If $V$ is a finite-dimensional vector space and $R, S, T \in \lin{V}$ are such that $RST$ is surjective, then $S$ is injective.
\end{exercise}

\begin{sol}
    Since $RST$ is surjective, and $V$ is finite dimensional, it follows that $RST$ is injective, hence invertible. By \autoref{ex:3d11}, then $RST = (RS)T$ is invertible if and only if $RS$ and $T$ are invertible. In particular, $RS$ is invertible, and applying \autoref{ex:3d11} again, we have that $R$ and $S$ are invertible. Hence, $S$ is injective.
\end{sol}

\begin{exercise}[3d15]
    Suppose $T \in \lin{V}$ and $v_1, \ldots, v_m$ is a list in $V$ such that $Tv_1, \ldots, Tv_m$ spans $V$. Prove that $v_1, \ldots, v_m$ spans $V$.
\end{exercise}

\begin{sol}
    Since $Tv_1, \ldots, Tv_m$ spans $V$, and $V$ is finite-dimensional, then $T$ is invertible. Then for every $v \in V$, there exist scalars $\alpha_1, \ldots, \alpha_m$ such that
    \[v = \alpha_1 Tv_1 + \cdots + \alpha_m Tv_m.\]
    Applying $T\inv$ to both sides, we have
    \[T\inv v = \alpha_1 v_1 + \cdots + \alpha_m v_m.\]
    Since $v$ was arbitrary, then $v_1, \ldots, v_m$ spans $V$.
\end{sol}

\begin{exercise}[3d16]
    Prove that every linear map from $\f^{n, 1}$ to $\f^{m, 1}$ is given by a matrix multiplication. In other words, prove that if $T \in \lin{\f^{n, 1}, \f^{m, 1}}$, then there exists an $m$-by-$n$ matrix $A$ such that $Tx = Ax$ for every $x \in \f^{n, 1}$.
\end{exercise}

\begin{sol}
    Let $e_1, \ldots, e_n$ be the standard basis of $\f^{n, 1}$. Define the $k$-th column of $A$ to be $Te_k \in \f^{m, 1}$ for $k = 1, \ldots, n$. Then for every $x \in \f^{n, 1}$, there exist scalars $\alpha_1, \ldots, \alpha_n$ such that
    \[x = \alpha_1 e_1 + \cdots + \alpha_n e_n.\]
    Applying $T$ to both sides, we have
    \[Tx = \alpha_1 Te_1 + \cdots + \alpha_n Te_n = A x,\]
    where the last equality follows from the definition of matrix multiplication. Hence, $Tx = Ax$ for every $x \in \f^{n, 1}$.
\end{sol}

\begin{exercise}[3d17]
    Suppose $V$ is finite-dimensional and $S \in \lin{V}$. Define $\ac \in \lin{\lin{V}}$ by
    \[\ac(T) = ST\]
    for $T \in \lin{V}$.
    \begin{subexercises}
        \item Show that $\dim \nul \ac = (\dim V)(\dim \nul S)$.
        \item Show that $\dim \range \ac = (\dim V)(\dim \range S)$.
    \end{subexercises}
\end{exercise}

\begin{sole}
    \item Consider $T \in \nul \ac$. Then $\ac(T) = ST = 0$, so $T$ is a linear map from $V$ to $\nul S$. Conversely, if $T$ is a linear map from $V$ to $\nul S$, then $ST = 0$, so $T \in \nul \ac$. Hence, $\nul \ac$ is the set of linear maps from $V$ to $\nul S$, and thus $\dim \nul \ac = (\dim V)(\dim \nul S)$.
    \item Consider $T \in \range \ac$. Then there exists some $U \in \lin{V}$ such that $\ac(U) = ST$. Since $ST$ is a linear map from $V$ to $\range S$, then $\range \ac$ is the set of linear maps from $V$ to $\range S$, and thus $\dim \range \ac = (\dim V)(\dim \range S)$.
\end{sole}

\begin{exercise}[3d18]
    Show that $V$ and $\lin{\f, V}$ are isomorphic vector spaces.
\end{exercise}

\begin{sol}
    Let $T : \lin{\f, V} \to V$ be defined by $T(\alpha) = \alpha(1)$ for $\alpha \in \lin{\f, V}$. We first show that $T$ is a linear map. Let $\alpha, \beta \in \lin{\f, V}$ and $\lambda \in \f$. Then
    \[T(\alpha + \beta) = (\alpha + \beta)(1) = \alpha(1) + \beta(1) = T\alpha + T\beta,\]
    and
    \[T(\lambda \alpha) = (\lambda \alpha)(1) = \lambda \alpha(1) = \lambda T\alpha.\]
    We now show that $T$ is an isomorphism. To see injectivity, let $\alpha, \beta \in \lin{\f, V}$ such that $T\alpha = T\beta$. Then $\alpha(1) = \beta(1)$. For any $x \in \f$, we have $\alpha(x) = x\alpha(1) = x\beta(1) = \beta(x)$, so $\alpha = \beta$. Hence, $T$ is injective.

    To see surjectivity, let $v \in V$. Define $\alpha \in \lin{\f, V}$ by $\alpha(x) = xv$ for $x \in \f$. Then $T\alpha = \alpha(1) = v$, so $T$ is surjective. Therefore, $T$ is an isomorphism, and thus $V$ and $\lin{\f, V}$ are isomorphic vector spaces.
\end{sol}

\begin{exercise}[3d19]
    Suppose $V$ is finite-dimensional and $T \in \lin{V}$. Prove that $T$ has the same matrix with respect to every basis of $V$ if and only if $T$ is a scalar multiple of the identity operator.

    \remark{This exercise has a beautiful alternate solution as follows: let $V$ have a basis $v_1, \ldots, v_n$. Consider the basis $w_1, \ldots, w_n$, where $w_i = v_j$ and $w_j = v_i$ for some $i \neq j$, and $w_k = v_k$ for $k \neq i, j$. One may perform similar calculations to deduce that the diagonal entries are equal to some $\lambda$, while every off-diagonal entry must be equal to some $\gamma$. The last step is to consider the basis $-v_1, v_2, \ldots, v_n$ to deduce that $\gamma = 0$, so that $T$ is a scalar multiple of the identity operator.}
\end{exercise}

\begin{sol}
    Suppose $T$ has the same matrix with respect to every basis of $V$. Then for any set of bases for $V$, its matrix must be the same. In particular, for any bases $v_1, \ldots, v_n$ and $u_1, \ldots, u_n$ of $V$, we have
    \[\mm(T, (v_1, \ldots, v_n)) = \mm(T, (u_1, \ldots, u_n)).\]
    Hence, we can declare that their matrix is just some $A$. We now consider the basis $v_1 + v_2, v_2, \ldots, v_n$, which yields the same matrix $A$. Let $w_1 = v_1 + v_2$ and $w_i = v_i$ for $i \geq 2$. In the new basis, we have the expression
    \[Tw_1 = A_{1, 1} w_1 + A_{2, 1} w_2 + \cdots + A_{n, 1} w_n = A_{1, 1} v_1 + (A_{1, 1} + A_{2, 1}) v_2 + A_{3, 1} v_3 + \cdots + A_{n, 1} v_n.\]
    This must equal the expression for $Tw_1 = Tv_1 + Tv_2$ in the original basis:
    \[Tv_1 + Tv_2 = (A_{1, 1} + A_{1, 2}) v_1 + (A_{2, 1} + A_{2, 2}) v_2 + \cdots + (A_{n, 1} + A_{n, 2}) v_n.\]
    Comparing coefficients of $v_1, \ldots, v_n$ in the two expressions, we get
    \begin{align*}
        A_{1, 1} &= A_{1, 1} + A_{1, 2}, \\
        A_{1, 1} + A_{2, 1} &= A_{2, 1} + A_{2, 2}, \\
        A_{j, 1} &= A_{j, 1} + A_{j, 2}~\text{for}~j \geq 3.
    \end{align*}
    From this, we obtain that $A_{1, 2} = 0, A_{2, 2} = A_{1, 1}$, and $A_{j, 2} = 0$ for $j \geq 3$, i.e., the diagonal elements $A_{1, 1}$ and $A_{2, 2}$ are equal, while off-diagonal entries in column 2 are 0. Now consider the basis $v_1, v_1 + v_2, \ldots, v_n$. Let $u_1 = v_1, u_2 = v_1 + v_2$, and $u_i = v_i$ for $i \geq 3$. In the new basis, we have
    \begin{align*}
        Tu_2 &= A_{1, 2}u_1 + \cdots + A_{n, 2}u_n \\
        &= A_{1, 2}v_1 + A_{2, 2}(v_1 + v_2) + A_{3, 2}v_3 + \cdots + A_{n, 2}v_n \\
        &= (A_{1, 2} + A_{2, 2})v_1 + A_{2, 2}v_2 + A_{3, 2}v_3 + \cdots + A_{n, 2}v_n. \\
        &= A_{1, 1}v_1 + A_{2, 2}v_2.
    \end{align*}
    This must equal the expression for $Tu_2 = Tv_1 + Tv_2$ in the original basis, whose expression is listed above. Comparing coefficients of $v_1$ and $v_2$, we get
    \begin{align*}
        A_{1, 1} &= A_{1, 1} + A_{1, 2}, \\
        A_{2, 2} &= A_{2, 1} + A_{2, 2}, \\ 
        A_{j, 2} &= A_{j, 1} + A_{j, 2} \quad \text{for } j \geq 3.
    \end{align*}
    From this, we obtain similar results about diagonal entries, but the off-diagonal entries in column 1 must also be 0. We may repeat the first process for $v_1 + v_k$ for $k \geq 3$ to get that entries off the diagonal in column $k$ must also be 0. Continuing this process, we conclude all off-diagonal entries are 0, and all diagonal entries are equal, i.e., $A$ is a scalar multiple of the identity matrix.

    Conversely, suppose $T$ is a scalar multiple of the identity operator. Then there exists some $\lambda \in \f$ such that $T = \lambda I$. For any basis of $V$, the matrix representation of $T$ with respect to that basis is the diagonal matrix with $\lambda$ on the diagonal. Hence, $T$ has the same matrix with respect to every basis of $V$.
\end{sol}

\begin{exercise}[3d20]
    Suppose $q \in \pp(\r)$. Prove that there exists a polynomial $p \in \pp(\r)$ such that
    \[q(x) = (x^2 + x) p''(x) + 2x p'(x) + p(3)\]
    for all $x \in \r$.
\end{exercise}

\begin{sol}
    Let $T : \pp_n(\r) \to \pp_n(\r)$ be defined by
    \[Tp = (x^2 + x) p'' + 2x p' + p(3)\]
    for $p \in \pp_n(\r)$. We first show that $T$ is a linear map. Let $p, q \in \pp_n(\r)$ and $\alpha \in \r$. Then
    \[T(p + q) = (x^2 + x) (p + q)'' + 2x (p + q)' + (p + q)(3) = Tp + Tq,\]
    and
    \[T(\alpha p) = (x^2 + x) (\alpha p)'' + 2x (\alpha p)' + (\alpha p)(3) = \alpha Tp.\]
    Then $T \in \lin{\pp_n(\r)}$. We now show that $T$ is invertible. To see injectivity, let $p \in \pp_n(\r)$ such that $Tp = 0$. Then
    \[(x^2 + x) p'' + 2x p' + p(3) = 0.\]
    Then
    \[(x^2 + x) p'' + 2x p' = -p(3).\]
    We analyze the degree of $p$ as follows:
    \begin{itemize}
        \item If $\deg p \geq 2$, consider $(x^2 + x)p''$. In particular, $(a_m x^m)'' = a_m m(m - 1)x^{m - 2}$, hence the coefficient of $x^m$ is $a_m m(m - 1)$. Moreover, $2xp'$ has coefficient $2m a_m$. Since $\deg p \geq 2$, then $m \geq 2$, so the total coefficient of $x^m$ is $a_m m(m - 1) + 2m a_m = a_m m(m - 1 + 2) = a_m m(m + 1)$. Since this is nonzero for $a_m \neq 0$, we get a contradiction with the right-hand side being a constant.
        \item If $\deg p = 1$, then $p(x) = ax + b$ for some $a, b \in \r$. Then $p''(x) = 0$ and $p'(x) = a$, so the left-hand side is $2ax$. Since the right-hand side is a constant, this is a contradiction.
        \item If $\deg p = 0$, then $p(x) = c$ for some $c \in \r$. Then $p''(x) = 0$ and $p'(x) = 0$, so the left-hand side is 0, and the right-hand side is $p(3) = c$. Hence, $c = 0$, and thus $p = 0$. Therefore, $T$ is injective.
    \end{itemize}
    Since $T$ is injective and $\pp_n(\r)$ is finite-dimensional, then $T$ is surjective, hence invertible. Then there does exist some $p \in \pp_n(\r)$ such that $Tp = q$.
\end{sol}

\begin{exercise}[3d21]
    Suppose $n$ is a positive integer and $A_{j, k} \in \f$ for all $j, k = 1, \ldots, n$. Prove that the following are equivalent (note that in both parts below, the number of equations equals the number of variables).
    \begin{subexercises}
        \item The trivial solution $x_1 = \cdots = x_n = 0$ is the only solution to the homogeneous system of equations
        \begin{align*}
            \sum_{k = 1}^{n} A_{1, k} x_k & = 0 \\
            \vdots \\
            \sum_{k = 1}^{n} A_{n, k} x_k & = 0
        \end{align*}
        \item For every $c_1, \ldots, c_n \in \f$, there exists a solution to the system of equations
        \begin{align*}
            \sum_{k = 1}^{n} A_{1, k} x_k & = c_1 \\
            \vdots \\
            \sum_{k = 1}^{n} A_{n, k} x_k & = c_n
        \end{align*}
    \end{subexercises}
\end{exercise}

\begin{sole}
    \item Suppose the trivial solution $0 \in \f^{n, 1}$ is the only solution to the homogeneous system of equations. Then $\nul T = \set 0$, where $T : \f^{n, 1} \to \f^{n, 1}$ is defined by $Tx = Ax$ for $x \in \f^{n, 1}$. Since $\nul T = \set 0$, then $T$ is injective. Since $\f^{n, 1}$ is finite-dimensional, then $T$ is surjective, hence invertible. Then for every $c_1, \ldots, c_n \in \f$, there exists some $x \in \f^{n, 1}$ such that $Tx = c$, where $c$ is the column vector with entries $c_1, \ldots, c_n$. Hence, there exists a solution to the system of equations.
    \item Suppose for every $c_1, \ldots, c_n \in \f$, there exists a solution to the system of equations. Then $T : \f^{n, 1} \to \f^{n, 1}$ defined by $Tx = Ax$ for $x \in \f^{n, 1}$ is surjective. Since $\f^{n, 1}$ is finite-dimensional, then $T$ is injective. Hence, the trivial solution is the only solution to the homogeneous system of equations.
\end{sole}

\begin{exercise}[3d22]
    Suppose $T \in \lin{V}$ and $v_1, \ldots, v_n$ is a basis of $V$. Prove that
    \[\mm(T, (v_1, \ldots, v_n))~\text{is invertible} \iff T~\text{is invertible}.\]
\end{exercise}

\begin{sol}
    Suppose $\mm(T, (v_1, \ldots, v_n))$ is invertible. Then there exists some $A \in \f^{n, n}$ such that $A\mm(T, (v_1, \ldots, v_n)) = I$. Let $U$ be the linear map from $V$ to $V$ whose matrix with respect to the basis $v_1, \ldots, v_n$ is $A$. Then
    \[\mm(UT, (v_1, \ldots, v_n)) = \mm(U, (v_1, \ldots, v_n))\mm(T, (v_1, \ldots, v_n)) = A\mm(T, (v_1, \ldots, v_n)) = I.\]
    Then $UT$ is the identity operator, and thus $T$ is injective. Since $V$ is finite-dimensional, then $T$ is surjective, hence invertible.

    Suppose $T$ is invertible. Then $T\inv$ exists, and we have
    \[\mm(T\inv T, (v_1, \ldots, v_n)) = \mm(T\inv, (v_1, \ldots, v_n))\mm(T, (v_1, \ldots, v_n)) = I.\]
    Hence, $\mm(T, (v_1, \ldots, v_n))$ is invertible.
\end{sol}

\begin{exercise}[3d23]
    Suppose that $u_1, \ldots, u_n$ and $v_1, \ldots, v_n$ are bases of $V$. Let $T \in \lin{V}$ be such that $Tv_k = u_k$ for each $k = 1, \ldots, n$. Prove that
    \[\mm(T, (v_1, \ldots, v_n)) = \mm(I, (u_1, \ldots, u_n), (v_1, \ldots, v_n)).\]
\end{exercise}

\begin{sol}
    By definition, column $k$ of $\mm(T, (v_1, \ldots, v_n))$ is $Tv_k = u_k$ with respect to the basis $v_1, \ldots, v_n$. Similarly, column $k$ of $\mm(I, (u_1, \ldots, u_n), (v_1, \ldots, v_n))$ is also $u_k$ with respect to the basis $v_1, \ldots, v_n$.
\end{sol}

\begin{exercise}[3d24]
    Suppose $A$ and $B$ are square matrices of the same size and $AB = I$. Prove that $BA = I$.
\end{exercise}

\begin{sol}
    Let $T : \f^{n, 1} \to \f^{n, 1}$ be defined by $Tx = Ax$ for $x \in \f^{n, 1}$. Since $AB = I$, then $T$ is surjective. Since $\f^{n, 1}$ is finite-dimensional, surjectivity implies injectivity. Hence, $T$ is invertible, and $T(Bx) = x = T(T\inv x)$. Then $Bx = T\inv x$ for every $x \in \f^{n, 1}$. Therefore,
    \[BAx = B(Tx) = T\inv (Tx) = x\]
    for every $x \in \f^{n, 1}$. Hence, $BA = I$.
\end{sol}