\section*{Preface}
\addcontentsline{toc}{section}{\protect\numberline{}Preface}

\textbf{Note: For any corrections, suggestions, or feedback regarding this solutions manual, readers are encouraged to reach out through the following channels:}
\begin{itemize}
    \item Discord Errata Server: \href{https://discord.gg/qecQk37vfm}{https://discord.gg/qecQk37vfm}
    \item Reddit: \href{https://www.reddit.com/user/ansv9a8fdh3/}{https://www.reddit.com/user/ansv9a8fdh3/}
    \item GitHub: \href{https://github.com/blanketism/Axler-Solutions}{https://github.com/blanketism/Axler-Solutions}
\end{itemize}

This solutions manual accompanies the fourth edition of Sheldon Axler's \emph{Linear Algebra Done Right}.
While several community-maintained solution sets exist for the third edition, the fourth edition introduces enough new and restructured material to warrant a dedicated resource--one written from scratch with the new text in mind.

This manual is written primarily for undergraduates encountering rigorous linear algebra for the first time.
Axler's text assumes little beyond mathematical maturity and a basic familiarity with proof writing.
There are some solutions in sections that may have mathematical identities that require additional background or insight, and these are explained as needed to ensure clarity and completeness.

A reader may notice certain notes underneath each exercise statement.
A guide is as follows:
\begin{itemize}
	\item \hint{These are hints (explicitly indicated, or otherwise) provided by Axler to guide the reader and assist in solving the exercise.}
	\item \note{Small excerpts written by Axler that either provide a reference to some term used in the problem, or offer additional context or clarification relevant to understanding the exercise.
	I have abstained from including every note provided.}
	\item \remark{These are remarks provided by myself to assist the reader in understanding the exercise, offering additional insights, clarifications, or alternative perspectives that may not be immediately apparent from the problem statement alone.}
\end{itemize}

The goal here is not to replace the work of reading and thinking.
Linear algebra, particularly in Axler's determinant-free, operator-theoretic style, rewards patience and independent struggle in ways that are difficult to replicate by reading someone else's solution.
This manual is best used after a genuine attempt at each problem, as a means of checking reasoning, identifying gaps, or becoming unstuck--not as a first resort.

Despite best efforts, mistakes are inevitable in any document of this scope: incorrect arguments, incomplete cases, notational slips, and the occasional solution that is simply wrong.
It has been some time since I first worked through Axler's text, and while I have made every effort to ensure accuracy, I recognize that errors may still exist.
Readers who encounter such mistakes are encouraged to report them through the channels listed above, and all contributions to improving this manual are greatly appreciated.

Finally, I am grateful to Professor Axler for writing a transformative text.
I recall my first experience with this text as an undergraduate, and it profoundly shaped my understanding and appreciation of linear algebra.
This solutions manual is my way of giving back and supporting future students in their journey through Axler's material.
I hope that it serves as a helpful companion, providing clarity and guidance while encouraging readers to engage deeply with the subject on their own terms.