\subsection{The Minimal Polynomial}

\begin{exercise}[5b1]
    Suppose $T \in \lin{V}$.
	Prove that $9$ is an eigenvalue of $T^2$ if and only if $3$ or $-3$ is an eigenvalue of $T$.
\end{exercise}

\begin{sol}
    Suppose $9$ is an eigenvalue of $T^2$.
	Then there exists a nonzero vector $v \in V$ such that $T^2 v = 9v$.
	This implies $(T - 3I)(T + 3I)v = 0$.
	Let $w = (T + 3I)v$, and suppose $w \neq 0$.
	Then
    \[
    	(T - 3I)w = Tw - 3w = 0 \implies Tw = 3w,
    \]
    showing that 3 is an eigenvalue of $T$.
	If $w = 0$, then $(T + 3I)v = 0$, which implies $Tv = -3v$, showing that $-3$ is an eigenvalue of $T$.

    Conversely, suppose 3 is an eigenvalue of $T$.
	Then there exists a nonzero vector $v \in V$ such that $Tv = 3v$.
	Applying $T$ again, we get $T^2 v = T(3v) = 3Tv = 3 \cdot 3v = 9v$, showing that $9$ is an eigenvalue of $T^2$.
	Similarly, if $-3$ is an eigenvalue of $T$, then $9$ is an eigenvalue of $T^2$.
\end{sol}

\begin{exercise}[5b2]
    Suppose $V$ is a complex vector space and $T \in \lin{V}$ has no eigenvalues.
	Prove that every subspace of $V$ invariant under $T$ is either $\set{0}$ or infinite-dimensional.
\end{exercise}

\begin{sol}
    Suppose $U$ is a subspace of $V$ invariant under $T$.
	If $U = \set{0}$, we are done.
	Suppose $U$ is nonzero and finite-dimensional.
	By invariance of $U$ under $T$, $T|_U \in \lin U$, and $T|_U$ has an eigenvalue $\lambda \in \cbb$ with corresponding eigenvector $v \in U$, $v \neq 0$.
	But then $v$ is also an eigenvector of $T$ with eigenvalue $\lambda$, contradicting the assumption that $T$ has no eigenvalues.
	Hence, any nonzero invariant subspace $U$ must be infinite-dimensional.
\end{sol}

\begin{exercise}[5b3]
    Suppose $n$ is a positive integer and $T \in \lin{\fbb^n}$ is defined by
    \[
    	T(x_1, \ldots, x_n) = (x_1 + \cdots + x_n, \ldots, x_1 + \cdots + x_n).
    \]
    \begin{subexercises}
        \item Find all eigenvalues and eigenvectors of $T$.
        \item Find the minimal polynomial of $T$.
    \end{subexercises}
\end{exercise}

\begin{sole}
    \item If $n = 1$, then $T(x_1) = (x_1)$, and the only eigenvalue is $1$ with corresponding eigenvectors being all nonzero vectors in $\fbb^1$.
    Otherwise, suppose $T(x_1, \ldots, x_n) = \lambda (x_1, \ldots, x_n)$ for some $\lambda \in \fbb$ and $(x_1, \ldots, x_n) \neq 0$.
	Then
    \[
    	\lambda x_j = x_1 + \cdots + x_n \quad \text{for all } j = 1, \ldots, n.
    \]
    This implies that $\lambda x_1 = \lambda x_2 = \cdots = \lambda x_n$.
	If $\lambda \neq 0$, then $x_1 = x_2 = \cdots = x_n$, and we can write $(x_1, \ldots, x_n) = (x_1, \ldots, x_1) = x_1(1, \ldots, 1)$.
	Substituting this into the eigenvalue equation gives
    \[
    	\lambda (x_1, \ldots, x_1) = T(x_1, \ldots, x_1) = (nx_1, \ldots, nx_1),
    \]
    which implies $\lambda = n$.
	If $\lambda = 0$, then $x_1 + \cdots + x_n = 0$, and the eigenvectors are all nonzero vectors $(x_1, \ldots, x_n)$ such that $x_1 + \cdots + x_n = 0$.
	Hence, the eigenvalues of $T$ are $0$ and $n$, with corresponding eigenvectors as described.
    \item If $n=1$, the minimal polynomial is $z-1$.

    For $n>1$, we know from (a) that the eigenvalues are $0$ and $n$. Then the minimal polynomial is a polynomial multiple of $z(z - n)$. Letting $x = x_1 + \cdots + x_n$, then
    \[
    	T(x_1, \ldots, x_n) = (x, \ldots, x), \quad (T - nI)(x_1, \ldots, x_n) = (x - nx_1, \ldots, x - nx_n).
    \]
    Observe that $(x - nx_1) + \cdots + (x - nx_n) = nx - n(x_1 + \cdots + x_n) = 0$.
	Therefore, $(T - nI)(x_1, \ldots, x_n)$ lies in $\nul T$, and applying $T$ again gives
    \[
    	T(T - nI)(x_1, \ldots, x_n) = 0.
    \]
    Hence, $z(z - n)$ is a polynomial multiple of the minimal polynomial, and since it must be monic, the minimal polynomial of $T$ is $z(z-n)$.
\end{sole}

\begin{exercise}[5b4]
    Suppose $\fbb = \cbb$, $T \in \lin{V}$, $p \in \pcal(\cbb)$, and $\alpha \in \cbb$.
	Prove that $\alpha$ is an eigenvalue of $p(T)$ if and only if $\alpha = p(\lambda)$ for some eigenvalue $\lambda$ of $T$.
\end{exercise}

\begin{sol}
    Suppose $\alpha$ is an eigenvalue of $p(T)$.
	Then there exists a nonzero vector $v \in V$ such that $p(T)v = \alpha v$.
	Then $p(T) - \alpha I$ is not injective.
    If $p(z) - \alpha = 0$, then $\alpha = p(\lambda)$ for any $\lambda \in \cbb$, and we are done.
    If $p(z) - \alpha = \beta$ for some constant $\beta \in \fbb$, then $p(T) - \alpha I = \beta I$ is injective, which contradicts the fact that $p(T) - \alpha I$ is not injective.
    We may now assume that $p(z) - \alpha$ is a nonconstant polynomial.
	By the Fundamental Theorem of Algebra, we can factor $p(z) - \alpha$ as
    \[
    	p(z) - \alpha = c(z - \lambda_1)(z - \lambda_2) \cdots (z - \lambda_m)
    \]
    for some $c \in \cbb \setminus \set{0}$ and $\lambda_1, \ldots, \lambda_m \in \cbb$.
	Then
    \[
    	p(T) - \alpha I = c(T - \lambda_1 I)(T - \lambda_2 I) \cdots (T - \lambda_m I).
    \]
    Since $p(T) - \alpha I$ is not injective, at least one of the factors on the right-hand side is not injective.
	Therefore, $T - \lambda_j I$ is not injective for some $j$, which means $\lambda_j$ is an eigenvalue of $T$.
	Then $p(\lambda_j) - \alpha = 0$, so $\alpha = p(\lambda_j)$ for some eigenvalue $\lambda_j$ of $T$.
    
    Conversely, suppose $\alpha = p(\lambda)$ for some eigenvalue $\lambda$ of $T$ with corresponding eigenvector $v$. Let $p(z) = a_m z^m + \cdots + a_1 z + a_0$. Since $T^m v = \lambda^m v$, we have
    \[
    	p(T)v = a_m T^m v + \cdots + a_1 T v + a_0 v = a_m \lambda^m v + \cdots + a_1 \lambda v + a_0 v = p(\lambda)v = \alpha v.
    \]
    Hence, $\alpha$ is an eigenvalue of $p(T)$.
\end{sol}

\begin{exercise}[5b5]
    Give an example of an operator on $\rbb^2$ that shows the result in Exercise 4 does not hold if $\cbb$ is replaced with $\rbb$.
\end{exercise}

\begin{sol}
    Consider the operator $T \in \lin{\rbb^2}$ defined by $T(x, y) = (-y, x)$, which represents a counterclockwise rotation by $90^\circ$.
	Observe that $T$ has no real eigenvalues as follows: If $(x, y)$ is an eigenvector of $T$ with eigenvalue $\lambda \in \rbb$, then $T(x, y) = \lambda (x, y)$ implies $(-y, x) = (\lambda x, \lambda y)$.
	This gives the system of equations:
    \[
    	-y = \lambda x \quad \text{and} \quad x = \lambda y.
    \]
    Since $x$ and $y$ cannot both be zero, one can work out that $\lambda^2 = -1$, which has no real solutions.
	Therefore, $T$ has no real eigenvalues.
	Now consider the polynomial $p(z) = z^2 + 1$.
	Then
    \[
    	p(T)(x, y) = T^2(x, y) + (x, y) = (-x, -y) + (x, y) = (0, 0).
    \]
    Thus, $0$ is an eigenvalue of $p(T)$ with corresponding eigenvector $(1, 0)$ (or any nonzero vector in $\rbb^2$).
	However, there is no real eigenvalue $\lambda$ of $T$ such that $p(\lambda) = 0$, since the eigenvalues of $T$ are complex.
	This example demonstrates that the result in \exref{5b4} does not hold when $\cbb$ is replaced with $\rbb$.
\end{sol}

\begin{exercise}[5b6]
    Suppose $T \in \lin{\fbb^2}$ is defined by $T(w, z) = (-z, w)$.
	Find the minimal polynomial of $T$.
\end{exercise}

\begin{sol}
    By the computation done in \exref{5b5}, we have $T^2(w, z) = (-w, -z)$, so $T^2 + I = 0$.
	Therefore, the polynomial $p(z) = z^2 + 1$ annihilates $T$.
	To see that this is the minimal polynomial, suppose $T = \alpha I$.
	Then $T(1, 0) = (0, 1) \neq \alpha(1, 0)$ for any $\alpha \in \fbb$, so $T \neq \alpha I$.
	Hence, the minimal polynomial of $T$ is $p(z) = z^2 + 1$.
\end{sol}

\begin{exercise}[5b7]
    \begin{subexercises}
        \item Give an example of $S, T \in \lin{\fbb^2}$ such that the minimal polynomial of $ST$ does not equal the minimal polynomial of $TS$.
        \item Suppose $V$ is finite-dimensional and $S, T \in \lin{V}$.
	Prove that if at least one of $S, T$ is invertible, then the minimal polynomial of $ST$ equals the minimal polynomial of $TS$.
    \end{subexercises}

    \hint{Show that if $S$ is invertible and $p \in \pcal(\fbb)$, then $p(TS) = S\inv p(ST) S$.}
\end{exercise}

\begin{sole}
    \item Consider the operators $S, T \in \lin{\fbb^2}$ defined by $S(w, z) = (0, w)$ and $T(w, z) = (w, 0)$.
	Then
    \[
    	ST(w, z) = S(w, 0) = (0, w) \quad \text{and} \quad TS(w, z) = T(0, w) = (0, 0).
    \]
    The minimal polynomial of $ST$ is $p(z) = z^2$, since $ST \neq 0$ but $(ST)^2 = 0$, while the minimal polynomial of $TS$ is $q(z) = z$.
	Hence, the minimal polynomials of $ST$ and $TS$ are not equal.
    \item Without loss of generality, suppose $S$ is invertible.
	We claim that $(TS)^n = S\inv (ST)^n S$ for all positive integers $n$.

	We prove this by induction on $n$.
	For the base case $n = 1$, we have $(TS)^1 = TS = S\inv (ST) S$.
	Now suppose the claim holds for some positive integer $k$, i.e., $(TS)^k = S\inv (ST)^k S$.
	Then
    \[
    	(TS)^{k+1} = (TS)^k (TS) = S\inv (ST)^k S (TS) = S\inv (ST)^k (ST) S = S\inv (ST)^{k+1} S.
    \]
    By induction, the claim holds for all positive integers $n$.
	Let $p = z^m + a_{m-1} z^{m-1} + \cdots + a_1 z + a_0$ be the minimal polynomial of $ST$.
	Then
    \begin{align*}
        p(TS) &= (TS)^m + a_{m-1} (TS)^{m-1} + \cdots + a_1 (TS) + a_0 I \\
        &= S\inv (ST)^m S + a_{m-1} S\inv (ST)^{m-1} S + \cdots + a_1 S\inv (ST) S + S\inv(a_0 I)S \\
        &= S\inv ((ST)^m + a_{m-1} (ST)^{m-1} + \cdots + a_1 (ST) + a_0 I) S \\
        &= S\inv p(ST) S = 0,
    \end{align*}
    where $S\inv S = I$ implies $S\inv (a_0I) S = a_0 I$.
	Hence, $p$ annihilates $TS$, and since $p$ is the minimal polynomial of $ST$, it follows that the minimal polynomial $q$ of $TS$ divides $p$.
	Observing that $ST = S(TS)S\inv$, we can similarly show that $q$ annihilates $ST$, and thus $p$ divides $q$.
	Therefore, $p = q$, and the minimal polynomials of $ST$ and $TS$ are equal.
\end{sole}

\begin{exercise}[5b8]
    Suppose $T \in \lin{\rbb^2}$ is the operator of counterclockwise rotation by $1^\circ$.
	Find the minimal polynomial of $T$.

    \note{Because $\dim \rbb^2 = 2$, the degree of the minimal polynomial of $T$ is at most $2$.
	Thus, the minimal polynomial of $T$ is not the tempting polynomial $x^{180} + 1$, even though $T^{180} = -I$.}
\end{exercise}

\begin{sol}
    Since $T$ is not a scalar multiple of the identity operator, the minimal polynomial of $T$ cannot have degree 1.
	Moreover, $\dim \rbb^2 = 2$ implies that the degree of the minimal polynomial of $T$ must be 2.
	Therefore, the minimal polynomial of $T$ is of the form
    \[
    	p(z) = z^2 + bz + c.
    \]
    Consider the point $(1, 0) \in \rbb^2$.
	Note that $T(x, y) = (x \cos 1^\circ - y \sin 1^\circ, x \sin 1^\circ + y \cos 1^\circ)$.
	Then
    \[
    	T(1, 0) = (\cos 1^\circ, \sin 1^\circ), \quad T^2(1, 0) = (\cos 2^\circ, \sin 2^\circ).
    \]
    Since $p(T) = 0$, we have
    \[
    	p(T)(1, 0) = T^2(1, 0) + bT(1, 0) + c(1, 0) = (\cos 2^\circ + b \cos 1^\circ + c, \sin 2^\circ + b \sin 1^\circ) = (0, 0).
    \]
    This gives the system of equations:
    \[
        \begin{cases}
            \cos 2^\circ + b \cos 1^\circ + c = 0, \\
            \sin 2^\circ + b \sin 1^\circ = 0.
        \end{cases}
    \]
    From this, we get the values of $b$ and $c$:
    \[
    	b = -\frac{\sin 2^\circ}{\sin 1^\circ} = -2 \cos 1^\circ, \quad c = -\cos 2^\circ - b \cos 1^\circ = 1.
    \]
    Therefore, the minimal polynomial of $T$ is $p(z) = z^2 - 2 \cos 1^\circ z + 1$.
\end{sol}

\begin{exercise}[5b9]
    Suppose $T \in \lin{V}$ is such that with respect to some basis of $V$, all entries of the matrix of $T$ are rational numbers.
	Explain why all coefficients of the minimal polynomial of $T$ are rational numbers.
\end{exercise}

\begin{sol}
    Let $A$ be the matrix of $T$ with respect to some basis of $V$.
	Since all entries of $A$ are rational numbers, $A^k$ also has rational entries for any positive integer $k$.
	Then the minimal polynomial $p(z) = z^m + a_{m-1} z^{m-1} + \cdots + a_1 z + a_0$ of $T$ in terms of the matrix $A$ satisfies
    \[
    	p(A) = A^m + a_{m-1} A^{m-1} + \cdots + a_1 A + a_0 I = 0.
    \]
    Then this gives a system of $(\dim V)^2$ linear equations in the coefficients $a_0, a_1, \ldots, a_{m-1}$ with rational coefficients.
	By uniqueness of the minimal polynomial, this system has a unique solution.
	Since the system has rational coefficients and a unique solution, the solution must also be rational.
	Therefore, all coefficients of the minimal polynomial of $T$ are rational numbers.
\end{sol}

\begin{exercise}[5b10]
    Suppose $V$ is finite-dimensional, $T \in \lin{V}$, and $v \in V$.
	Prove that
    \[
    	\spn(v, Tv, \ldots, T^m v) = \spn(v, Tv, \ldots, T^{\dim V - 1} v)
    \]
    for all integers $m \geq \dim V - 1$.
\end{exercise}

\begin{sol}
    Let $n=\dim V$ and let $p(z)=z^d+a_{d-1}z^{d-1}+\cdots+a_0$ be the minimal polynomial of $T$.
	Then $d \leq n$ and $p(T)=0$.
	For any $v \in V$,
    \[
    	p(T)v=0 \implies T^d v=-a_{d-1} T^{d-1} v-\cdots-a_1 Tv-a_0 v \implies T^d v \in \operatorname{span}\left(v, Tv, \dots, T^{d-1} v \right).
    \]
    Let $U=\operatorname{span}\left(v, Tv, \dots, T^{d-1} v\right)$.

    We claim that $U$ is invariant under $T$.
	Take any $u=c_0 v+c_1 Tv+\cdots+c_{d-1} T^{d-1} v \in U$.
	Then,
    \[
    	Tu=c_0 Tv+c_1 T^2 v+\cdots+c_{d-2} T^{d-1} v+c_{d-1} T^d v.
    \]
    Every term on the right-hand side except $T^d v$ is automatically in the spanning set of $U$.
	We also showed that $T^d v \in U$ earlier, so $Tu \in U$.
	Hence, $T(U) \subseteq U$.

    Because $v \in U$ and $U$ is invariant under $T$, we see that $T^m v \in U$ for every $m \geq 0$ (this is immediate by induction).
	So, for any $m \geq n-1$, we have that
    \[
    	\operatorname{span}(v, Tv, \dots, T^m v) \subseteq U \subseteq \operatorname{span}(v, Tv, \dots, T^{n-1}v)
    \]
    by using $d-1 \leq n-1$ to obtain the second inclusion.
	Since $\{v, Tv, \dots, T^{n-1} v\} \subseteq \{v, Tv, \dots, T^m v\}$, the reverse inclusion is immediate, and so
    \[
    	\operatorname{span}(v, Tv, \dots, T^m v)=\operatorname{span}(v, Tv, \dots, T^{n-1}v). \qh
    \]
\end{sol}

\begin{exercise}[5b11]
    Suppose $V$ is a two-dimensional vector space, $T \in \lin{V}$, and the matrix of $T$ with respect to some basis of $V$ is $\begin{pmatrix} a & c \\ b & d \end{pmatrix}$.
    \begin{subexercises}
        \item Show that $T^2 - (a + d)T + (ad - bc)I = 0$.
        \item Show that the minimal polynomial of $T$ equals
        \[
            \begin{cases}
                z - a & \text{if } b = c = 0 \text{ and } a = d, \\
                z^2 - (a + d)z + (ad - bc) & \text{otherwise.}
            \end{cases}
        \]
    \end{subexercises}
\end{exercise}

\begin{sole}
    \item We compute $T^2$:
    \[
        T^2 = 
        \begin{pmatrix}
            a & c \\
            b & d
        \end{pmatrix}
        \begin{pmatrix}
            a & c \\
            b & d
        \end{pmatrix}
        =
        \begin{pmatrix}
            a^2 + bc & ac + cd \\
            ab + bd & bc + d^2
        \end{pmatrix}.
    \]
    Then 
    \begin{align*}
        T^2 - (a + d)T + (ad - bc)I &= 
        \begin{pmatrix}
            a^2 + bc & ac + cd \\
            ab + bd & bc + d^2
        \end{pmatrix}
        - (a + d)
        \begin{pmatrix}
            a & c \\
            b & d
        \end{pmatrix}
        + (ad - bc)
        \begin{pmatrix}
            1 & 0 \\
            0 & 1
        \end{pmatrix} \\
        &= 
        \begin{pmatrix}
            a^2 + bc - (a + d)a + ad - bc & ac + cd - (a + d)c \\
            ab + bd - (a + d)b & bc + d^2 - (a + d)d + ad - bc
        \end{pmatrix} \\
        &=
        \begin{pmatrix}
            a^2 + bc - a^2 - ad + ad - bc & ac + cd - ac - cd \\
            ab + bd - ab - bd & bc + d^2 - d^2 - ad + ad - bc
        \end{pmatrix} \\
        &= 
        \begin{pmatrix}
            0 & 0 \\
            0 & 0
        \end{pmatrix}.
    \end{align*}
    \item If $b = c = 0$ and $a = d$, then the matrix of $T$ is
    \[
        \begin{pmatrix}
            a & 0 \\ 
            0 & a 
        \end{pmatrix},
    \]
    which is a scalar multiple of the identity matrix.
    In this case, the minimal polynomial of $T$ is $z - a$.

    Otherwise, the polynomial $z^2 - (a + d)z + (ad - bc)$ annihilates $T$ by part (a).
    To see that this is the minimal polynomial, we need to check that $T$ is not a scalar multiple of the identity matrix.
    If $T$ were a scalar multiple of the identity matrix, then we would have $b = c = 0$ and $a = d$, which contradicts our assumption.
    Therefore, the minimal polynomial of $T$ has degree 2 and is $z^2 - (a + d)z + (ad - bc)$ in this case.
\end{sole}

\begin{exercise}[5b12]
    Define $T \in \lin{\fbb^n}$ by $T(x_1, x_2, x_3, \ldots, x_n) = (x_1, 2x_2, 3x_3, \ldots, nx_n)$.
	Find the minimal polynomial of $T$.
\end{exercise}

\begin{sol}
    For each $k \in \{1, \dots, n\}$, the standard basis vector $e_k$ satisfies $Te_k=ke_k$, so each $k$ is an eigenvalue. Let $p(z)=(z-1)(z-2) \cdots (z-n)$. So,
    \[
    	p(T) e_k=p(k) e_k=0 \cdot e_k=0 \text{ for all } k \in \{1, \dots, n\},
    \]
    and since the $e_k$ form a basis of $V$, $p(T)=0$. Therefore, the minimal polynomial $m_T (z)$ divides $p(z)$.

    Now suppose $m_T (z)$ is the minimal polynomial of $T$. For each eigenvalue $k$,
    \[
    	0=m_T (T) e_k=m_T (k) e_k \implies m_T (k)=0.
    \]
    Thus, $(z-k)$ divides $m_T (z)$ for every $k \in \{1, \dots, n\}$. Because the factors are distinct, $p(z)$ divides $m_T (z)$.

    Since both $p(z)$ and $m_T (z)$ are monic, $p(z)=m_T (z)$. Hence, the minimal polynomial is $p(z)=(z-1) \cdots (z-n)$.
\end{sol}

\begin{exercise}[5b13]
    Suppose $T \in \lin{V}$ and $p \in \pcal(\fbb)$.
	Prove that there exists a unique $r \in \pcal(\fbb)$ such that $p(T) = r(T)$ and $\deg r$ is less than the degree of the minimal polynomial of $T$.
\end{exercise}

\begin{sol}
    Let $m$ be the minimal polynomial of $T$ with degree $d$.
    By the Division Algorithm for polynomials, we can write
    \[
    	p(z) = q(z)m(z) + r(z),
    \]
    where $q, r \in \pcal(\fbb)$ and $\deg r < d$.
    Applying this to $T$, we have
    \[
    	p(T) = q(T)m(T) + r(T).
    \]
    Since $m(T) = 0$, it follows that
    \[
    	p(T) = r(T).
    \]
    Thus, there exists a polynomial $r$ such that $p(T) = r(T)$ and $\deg r < d$.

    To show uniqueness, suppose there exists another polynomial $s \in \pcal(\fbb)$ such that $p(T) = s(T)$ and $\deg s < d$.
    Then we have
    \[
    	r(T) = p(T) = s(T).
    \]
    This implies that $(r - s)(T) = 0$.
    Since $\deg(r - s) < d$, it follows that $r - s$ must be the zero polynomial (otherwise, it would contradict the minimality of $m$).
    Hence, $r = s$, proving uniqueness.
\end{sol}

\begin{exercise}[5b14]
    Suppose $V$ is finite-dimensional and $T \in \lin{V}$ has minimal polynomial $4 + 5z - 6z^2 - 7z^3 + 2z^4 + z^5$.
	Find the minimal polynomial of $T\inv$.
\end{exercise}

\begin{sol}
    Let $p(z) = 4 + 5z - 6z^2 - 7z^3 + 2z^4 + z^5$ be the minimal polynomial of $T$.
    We want to find the minimal polynomial of $T\inv$.
    Since $p(z)$ is the minimal polynomial of $T$, we have
    \[
    	p(T) = 4I + 5T - 6T^2 - 7T^3 + 2T^4 + T^5 = 0.
    \]
    To find the minimal polynomial of $T\inv$, apply $T\inv$ to both sides of the equation until we express it in terms of $T\inv$:
    \[
    	4T^{-5} + 5T^{-4} - 6T^{-3} - 7T^{-2} + 2T^{-1} + I = 0.
    \]
    Then the polynomial $q(z) = 4z^5 + 5z^4 - 6z^3 - 7z^2 + 2z + 1$ annihilates $T\inv$.
    To make it monic, we can divide by the leading coefficient:
    \[
    	q(z) = z^5 + \frac{5}{4}z^4 - \frac{3}{2}z^3 - \frac{7}{4}z^2 + \frac{1}{2}z + \frac{1}{4}.
    \]
    Suppose $T\inv$ has a minimal polynomial $m(z)$ with $\deg m < 5$, hence $m(T\inv) = 0$.
    Applying $T^{\deg m}$ to both sides gives $n(T) = 0$ for some polynomial $n(z)$ of degree less than 5, which contradicts the minimality of $p(z)$.
    Therefore, the minimal polynomial of $T\inv$ is $q(z)$.
\end{sol}

\begin{exercise}[5b15]
    Suppose $V$ is a finite-dimensional complex vector space with $\dim V > 0$ and $T \in \lin{V}$.
	Define $f: \cbb \to \rbb$ by
    \[
    	f(\lambda) = \dim \range(T - \lambda I).
    \]
    Prove that $f$ is not a continuous function.
\end{exercise}

\begin{sol}
    Since $V$ is a finite-dimensional complex vector space, the operator $T$ has at least one eigenvalue $\lambda_0 \in \cbb$.
    By \exref{5a11}, there exists $\delta > 0$ such that $T - \lambda I$ is invertible for all $\lambda \in \cbb$ with $0 < |\lambda - \lambda_0| < \delta$.
    This implies that for all such $\lambda$, we have $\dim \range(T - \lambda I) = \dim V$.
    However, at the eigenvalue $\lambda_0$, we have $\dim \range(T - \lambda_0 I) < \dim V$ since $\dim \nul(T - \lambda_0 I) > 0$.
    Therefore,
    \[
    	\lim_{\lambda \to \lambda_0} f(\lambda) \neq f(\lambda_0),
    \]
    which shows that $f$ is not continuous at $\lambda_0$.
\end{sol}

\begin{exercise}[5b16]
    Suppose $a_0, \ldots, a_{n-1} \in \fbb$.
	Let $T$ be the operator on $\fbb^n$ whose matrix (with respect to the standard basis) is
    \[
        \begin{pmatrix}
            0 & & & & & -a_0 \\
            1 & 0 & & & & -a_1 \\
            & 1 & \ddots & & & -a_2 \\
            & & \ddots & & & \vdots \\
            & & & & 0 & -a_{n-2} \\
            & & & & 1 & -a_{n-1}
        \end{pmatrix}.
    \]
    Here all entries of the matrix are $0$ except for all $1$'s on the line under the diagonal and the entries in the last column (some of which might also be $0$).
	Show that the minimal polynomial of $T$ is the polynomial
    \[
    	a_0 + a_1 z + \cdots + a_{n-1} z^{n-1} + z^n.
    \]
\end{exercise}

\begin{sol}
    Let $p(z) = a_0 + a_1 z + \cdots + a_{n-1} z^{n-1} + z^n$.
    Let $e_1, \ldots, e_n$ be the standard basis of $\fbb^n$.
    We will show that $p(T) = 0$ and that no polynomial of lower degree annihilates $T$.
    First, we compute $T^k e_1$ for $k = 0, 1, \ldots, n$:
    \[
    	T^0 e_1 = e_1, \quad T^1 e_1 = e_2, \quad T^2 e_1 = e_3, \quad \ldots, \quad T^{n-1} e_1 = e_n, \quad T^n e_1 = -a_0 e_1 - a_1 e_2 - \cdots - a_{n-1} e_n.
    \]
    Then we have
    \begin{align*}
        p(T)e_1 &= a_0 T^0 e_1 + a_1 T^1 e_1 + \cdots + a_{n-1} T^{n-1} e_1 + T^n e_1 \\
        &= a_0 e_1 + a_1 e_2 + \cdots + a_{n-1} e_n - a_0 e_1 - a_1 e_2 - \cdots - a_{n-1} e_n \\
        &= 0.
    \end{align*}
    Since $T^{j-1} e_1 = e_j$ for $j = 1, 2, \ldots, n$, and $p(T)$ commutes with $T$, we have
    \[
    	p(T)e_j = p(T)T^{j-1} e_1 = T^{j-1} p(T) e_1 = T^{j-1} 0 = 0
    \]
    for all $j = 1, 2, \ldots, n$.
    Since $\{e_1, e_2, \ldots, e_n\}$ is a basis for $\fbb^n$, it follows that $p(T) = 0$.

    To show that $p$ is the minimal polynomial, suppose there exists a polynomial $q(z) = b_0 + b_1 z + \cdots + b_{m-1} z^{m-1} + z^m$ of degree $m < n$ such that $q(T) = 0$.
    Then we would have
    \[
    	q(T)e_1 = b_0 e_1 + b_1 e_2 + \cdots + b_{m-1} e_m + T^m e_1 = 0.
    \]
    However, $T^m e_1 = e_{m+1}$, which is not in the span of $\{e_1, e_2, \ldots, e_m\}$ since $m < n$.
    This leads to a contradiction, as $e_{m+1}$ cannot be expressed as a linear combination of $e_1, e_2, \ldots, e_m$.
    Therefore, no polynomial of degree less than $n$ annihilates $T$, and the minimal polynomial of $T$ is indeed $p(z) = a_0 + a_1 z + \cdots + a_{n-1} z^{n-1} + z^n$.
\end{sol}

\begin{exercise}[5b17]
    Suppose $V$ is finite-dimensional, $T \in \lin{V}$, and $p$ is the minimal polynomial of $T$.
	Suppose $\lambda \in \fbb$.
	Show that the minimal polynomial of $T - \lambda I$ is the polynomial $q$ defined by $q(z) = p(z + \lambda)$.
\end{exercise}

\begin{sol}
    Let $p(z)$ be the minimal polynomial of $T$.
    Then we have
    \[
    	p(T) = 0.
    \]
    Consider the polynomial $q(z) = p(z + \lambda)$.
    Then we have
    \[
    	q(T - \lambda I) = p((T - \lambda I) + \lambda I) = p(T) = 0.
    \]
    Thus, $q$ annihilates $T - \lambda I$.

    To show that $q$ is the minimal polynomial, suppose there exists a polynomial $r(z)$ of degree less than $\deg q$ such that $r(T - \lambda I) = 0$.
    Then we can write
    \[
    	s(z) = r(z - \lambda)
    \]
    for some polynomial $s(z)$ of degree less than $\deg p$.
    Then we have
    \[
    	s(T) = r(T - \lambda I) = 0.
    \]
    However, this contradicts the minimality of $p$, since $\deg s < \deg p$ and $s(T) = 0$.
    Therefore, no polynomial of degree less than $\deg q$ annihilates $T - \lambda I$, and the minimal polynomial of $T - \lambda I$ is indeed $q(z) = p(z + \lambda)$.
\end{sol}

\begin{exercise}[5b18]
    Suppose $V$ is finite-dimensional, $T \in \lin{V}$, and $p$ is the minimal polynomial of $T$.
	Suppose $\lambda \in \fbb \setminus \set{0}$.
	Show that the minimal polynomial of $\lambda T$ is the polynomial $q$ defined by $q(z) = \lambda^{\deg p} p (\frac{z}{\lambda})$.
\end{exercise}

\begin{sol}
    Let $p(z)$ be the minimal polynomial of $T$.
    Then we have
    \[
    	p(T) = 0.
    \]
    Consider the polynomial $q(z) = \lambda^{\deg p} p(\frac{z}{\lambda})$.
    Then we have
    \[
    	q(\lambda T) = \lambda^{\deg p} p\left(\frac{\lambda T}{\lambda}\right) = \lambda^{\deg p} p(T) = 0.
    \]
    Moreover, $q$ has leading term $\lambda^{\deg p}(\frac z{\lambda})^{\deg p} = z^{\deg p}$, so $q$ is monic and has the same degree as $p$.
    To show that $q$ is the minimal polynomial, suppose there exists a polynomial $r(z)$ of degree less than $\deg q$ such that $r(\lambda T) = 0$.
    Define $s(z) = r(\lambda z)$.
    Then we have
    \[
    	s(T) = r(\lambda T) = 0.
    \]
    However, $\deg s = \deg r < \deg q = \deg p$, which contradicts the minimality of $p$.
    Therefore, no polynomial of degree less than $\deg q$ annihilates $\lambda T$, and the minimal polynomial of $\lambda T$ is indeed $q(z) = \lambda^{\deg p} p(\frac{z}{\lambda})$.
\end{sol}

\begin{exercise}[5b19]
    Suppose $V$ is finite-dimensional and $T \in \lin{V}$.
	Let $\ecal$ be the subspace of $\lin{V}$ defined by
    \[
    	\ecal = \set{q(T) \mid q \in \pcal(\fbb)}.
    \]
    Prove that $\dim \ecal$ equals the degree of the minimal polynomial of $T$.
\end{exercise}

\begin{sol}
    Let $p(z)$ be the minimal polynomial of $T$ with degree $d$.
    We will show that $\dim \ecal = d$.

    First, we show that $\dim \ecal \leq d$.
    By the Division Algorithm for polynomials, for any polynomial $q \in \pcal(\fbb)$, we can write
    \[
    	q(z) = s(z)p(z) + r(z),
    \]
    where $s, r \in \pcal(\fbb)$ and $\deg r < d$.
    Then we have
    \[
    	q(T) = s(T)p(T) + r(T) = 0 + r(T) = r(T).
    \]
    Since $\deg r < d$, the set $\{I, T, T^2, \ldots, T^{d-1}\}$ spans $\ecal$.
    Hence, $\dim \ecal \leq d$.

    Next, we show that $\dim \ecal \geq d$.
    Suppose there exists a nontrivial linear combination of $\{I, T, T^2, \ldots, T^{d-1}\}$ that equals zero:
    \[
    	a_0 I + a_1 T + a_2 T^2 + \cdots + a_{d-1} T^{d-1} = 0.
    \]
    This would imply that the polynomial
    \[
    	q(z) = a_0 + a_1 z + a_2 z^2 + \cdots + a_{d-1} z^{d-1}
    \]
    annihilates $T$, contradicting the minimality of $p(z)$ since $\deg q < d$.
    Therefore, the set $\{I, T, T^2, \ldots, T^{d-1}\}$ is linearly independent in $\ecal$, which implies that $\dim \ecal \geq d$.

    Combining both inequalities, we conclude that $\dim \ecal = d$, which is the degree of the minimal polynomial of $T$.
\end{sol}

\begin{exercise}[5b20]
    Suppose $T \in \lin{\fbb^4}$ is such that the eigenvalues of $T$ are $3, 5, 8$.
	Prove that $(T - 3I)^2(T - 5I)^2(T - 8I)^2 = 0$.
\end{exercise}

\begin{sol}
    Let $p$ be the minimal polynomial of $T$.
    The eigenvalues of $T$ are $3$, $5$, and $8$, so each is a root of $p$.
    Hence,
    \[
    	p(z)=(z-3)^{m_1} (z-5)^{m_2} (z-8)^{m_3}
    \]
    where $m_1$, $m_2$, $m_3 \geq 1$.
    Because $T$ acts on a $4$-dimensional space, $\deg p \leq 4$, and so $m_1+m_2+m_3 \leq 4$.
    Since $m_2$, $m_3 \geq 1$, we have $m_1 \leq 4-1-1=2$.
    By similar logic, $m_1$, $m_2$, $m_3 \leq 2$.
    This means $p(z)$ divides $(z-3)^2 (z-5)^2 (z-8)^2$.
    Applying this polynomial to $T$ yields
    \[
    	(T-3I)^2 (T-5I)^2 (T-8I)^2=0. \qh
    \]
\end{sol}

\begin{exercise}[5b21]
    Suppose $V$ is finite-dimensional and $T \in \lin{V}$.
	Prove that the minimal polynomial of $T$ has degree at most $1 + \dim \range T$.

    \note{If $\dim \range T < \dim V - 1$, then this exercise gives a better upper bound than 5.22 for the degree of the minimal polynomial of $T$.}
\end{exercise}

\begin{sol}
    Let $r = \dim \range T$.
    Observe that $\range T$ is invariant under $T$, and we can consider the restriction of $T$ to $\range T$, denoted by $T|_{\range T}$.
    Let $p(z)$ be the minimal polynomial of $T$ and let $q(z)$ be the minimal polynomial of $T|_{\range T}$.
    Then $\deg q \leq r$ since $T|_{\range T}$ is an operator on a space of dimension $r$.

    We now show that the polynomial $zq(z)$ annihilates $T$.
    For any $v \in V$, we know that $Tv \in \range T$.
    By invariance, we know that $w \in \range T$ implies $(T|_{\range T})^k w \in \range T$ for any $k \geq 0$.
    Then
    \[
    	q(T)w = q(T|_{\range T})w = 0.
    \]
    Therefore, for any $v \in V$, we have
    \[
    	zq(z)(T)v = T q(T)v = q(T) Tv = 0,
    \]
    where we used the fact that $T$ commutes with $q(T)$ since $q(T)$ is a polynomial in $T$.
    This shows that $zq(z)$ annihilates $T$, and hence the minimal polynomial $p(z)$ of $T$ divides $zq(z)$.
    Since $\deg q \leq r$, we have $\deg p \leq 1 + r = 1 + \dim \range T$.
\end{sol}

\begin{exercise}[5b22]
    Suppose $V$ is finite-dimensional and $T \in \lin{V}$.
	Prove that $T$ is invertible if and only if $I \in \spn(T, T^2, \ldots, T^{\dim V})$.
\end{exercise}

\begin{sol}
    Suppose $T$ is invertible.
    Let $q(z)$ be the minimal polynomial of $T$.
    Since $T$ is invertible, $0$ is not an eigenvalue of $T$, and thus $q(0) \neq 0$.
    We may write $q(z)$ as
    \[
    	q(z) = z^m + a_{m-1} z^{m-1} + \cdots + a_1 z + a_0,
    \]
    where $a_0 \neq 0$ and $m \leq \dim V$.
    Then we have
    \[
    	0 = q(T) = T^m + a_{m-1} T^{m-1} + \cdots + a_1 T + a_0 I.
    \]
    Rearranging gives
    \[
    	I = -\frac{1}{a_0} (T^m + a_{m-1} T^{m-1} + \cdots + a_1 T) \in \spn(T, T^2, \ldots, T^m) \subseteq \spn(T, T^2, \ldots, T^{\dim V}).
    \]
    Hence, if $T$ is invertible, then $I \in \spn(T, T^2, \ldots, T^{\dim V})$.

    Conversely, suppose $I \in \spn(T, T^2, \ldots, T^{\dim V})$.
    Then there exist scalars $a_1, a_2, \ldots, a_{\dim V}$ such that
    \[
    	I = a_1 T + a_2 T^2 + \cdots + a_{\dim V} T^{\dim V}.
    \]
    Rearranging gives
    \[
    	0 = -I + a_1 T + a_2 T^2 + \cdots + a_{\dim V} T^{\dim V} = p(T),
    \]
    where $p(z) = -1 + a_1 z + a_2 z^2 + \cdots + a_{\dim V} z^{\dim V}$.
    Since the minimal polynomial of $T$ divides any polynomial that annihilates $T$, the minimal polynomial of $T$ must also have a nonzero constant term.
    Therefore, $0$ is not an eigenvalue of $T$, and hence $T$ is invertible.
\end{sol}

\begin{exercise}[5b23]
    Suppose $V$ is finite-dimensional and $T \in \lin{V}$.
	Let $n = \dim V$.
	Prove that if $v \in V$, then $\spn(v, Tv, \ldots, T^{n-1}v)$ is invariant under $T$.
\end{exercise}

\begin{sol}
    Let $W = \spn(v, Tv, \ldots, T^{n-1}v)$.
    To show that $W$ is invariant under $T$, we may show that $Tv, T^2v, \ldots, T^nv \in W$.
    Observe that $Tv, T(Tv) = T^2v, T(T^2v) = T^3v, \ldots, T(T^{n-2}v) = T^{n-1}v$ are all in $W$ by definition.
    It remains to show that $T^nv \in W$.

    Let $p(z)$ be the minimal polynomial of $T$.
    Let $m = \deg p$.
    Since $m \leq n$, we have
    \[
    	p(T)v = T^m v + a_{m-1} T^{m-1} v + \cdots + a_1 Tv + a_0 v = 0.
    \]
    Rearranging gives
    \[
    	T^m v = -a_{m-1} T^{m-1} v - \cdots - a_1 Tv - a_0 v \in W.
    \]
    If $m = n$, then we are done.
    If $m < n$, then we can apply $T^{n-m}$ to both sides to get
    \[
    	T^n v = -a_{m-1} T^{n-1} v - \cdots - a_1 T^{n-m+1} v - a_0 T^{n-m} v \in W,
    \]
    where we used the fact that $T^{n-m}v, T^{n-m+1}v, \ldots, T^{n-1}v \in W$ since $n-m < n$.
    Therefore, $T^nv \in W$, and hence $W$ is invariant under $T$.
\end{sol}

\begin{exercise}[5b24]
    Suppose $V$ is a finite-dimensional complex vector space.
	Suppose $T \in \lin{V}$ is such that $5$ and $6$ are eigenvalues of $T$ and that $T$ has no other eigenvalues.
	Prove that $(T - 5I)^{\dim V - 1}(T - 6I)^{\dim V - 1} = 0$.
\end{exercise}

\begin{sol}
    Let $p$ be the minimal polynomial of $T$. The eigenvalues of $T$ are $5$ and $6$, so each is a root of $p$.
    Hence,
    \[
    	p(z) = (z - 5)^{m_1}(z - 6)^{m_2}
    \]
    where $m_1, m_2 \geq 1$.
    Because $\deg p \leq \dim V$, we have $m_1 + m_2 \leq \dim V$.
    Since $m_2 \geq 1$, we get $m_1 \leq \dim V - 1$, and similarly $m_2 \leq \dim V - 1$.
    This means $p(z)$ divides $(z - 5)^{\dim V - 1}(z - 6)^{\dim V - 1}$, so
    \[
    	(T - 5I)^{\dim V - 1}(T - 6I)^{\dim V - 1} = 0. \qh
    \]
\end{sol}

\begin{exercise}[5b25]
    Suppose $V$ is finite-dimensional, $T \in \lin{V}$, and $U$ is a subspace of $V$ that is invariant under $T$.
    \begin{subexercises}
        \item Prove that the minimal polynomial of $T$ is a polynomial multiple of the minimal polynomial of the quotient operator $T / U$.
        \item Prove that
        \[
        	(\text{minimal polynomial of } T|_U) \times (\text{minimal polynomial of } T / U)
        \]
        is a polynomial multiple of the minimal polynomial of $T$.
    \end{subexercises}
    \note{The quotient operator $T / U$ was defined \emph{\exref{5a38}}.}
\end{exercise}

\begin{sole}
    \item Let $p(z)$ be the minimal polynomial of $T$ and let $q(z)$ be the minimal polynomial of $T / U$.
    Recall that $T / U$ is defined by $(T / U)(v + U) = Tv + U$ for all $v \in V$.
    Inductively, we have $(T / U)^k(v + U) = T^k v + U$ for all $k \geq 0$.
    Then we have
    \[
    	p(T / U)(v + U) = p(T)v + U = 0 + U = U,
    \]
    where we used the fact that $p(T) = 0$.
    Therefore, $p(T / U) = 0$, which implies that $q(z)$ divides $p(z)$.
    Hence, the minimal polynomial of $T$ is a polynomial multiple of the minimal polynomial of the quotient operator $T / U$.
    \item Let $p(z)$ be the minimal polynomial of $T$, let $q(z)$ be the minimal polynomial of $T|_U$, and let $r(z)$ be the minimal polynomial of $T / U$.
    By definition,
    \[
    	r(T / U)(v + U) = r(T)v + U = U,
    \]
    where we used the fact that $r(T / U) = 0$.
    Then $r(T)v \in U$ for all $v \in V$.
    Moreover, invariance of $U$ under $T$ implies that $q(T)u = q(T|_U)u = 0$ for all $u \in U$.
    Since $r(T)v \in U$, and $q(T) = q(T|_U)$ on $U$, we have
    \[
    	q(T)r(T)v = q(T|_U)r(T)v = 0
    \]
    for all $v \in V$.
    Therefore, $q(T)r(T) = 0$, which implies $p(z)$ divides $q(z)r(z)$.
    Hence, the product of the minimal polynomials of $T|_U$ and $T / U$ is a polynomial multiple of the minimal polynomial of $T$.
\end{sole}

\begin{exercise}[5b26]
    Suppose $V$ is finite-dimensional, $T \in \lin{V}$, and $U$ is a subspace of $V$ that is invariant under $T$.
	Prove that the set of eigenvalues of $T$ equals the union of the set of eigenvalues of $T|_U$ and the set of eigenvalues of $T / U$.
\end{exercise}

\begin{sol}
    Let $\lambda$ be an eigenvalue of $T$ with corresponding eigenvector $v \in V \setminus \{0\}$.
    Then we have
    \[
    	Tv = \lambda v.
    \]
    If $v \in U$, then $\lambda$ is an eigenvalue of $T|_U$.
    If $v \notin U$, then consider the coset $v + U \in V / U$.
    We have
    \[
    	(T / U)(v + U) = Tv + U = \lambda v + U = \lambda (v + U),
    \]
    which shows that $\lambda$ is an eigenvalue of $T / U$.

    Conversely, suppose $\lambda$ is an eigenvalue of $T|_U$ with corresponding eigenvector $u \in U \setminus \{0\}$.
    Then we have
    \[
    	T|_U u = Tu = \lambda u,
    \]
    which shows that $\lambda$ is also an eigenvalue of $T$.

    Now suppose $\lambda$ is an eigenvalue of $T / U$ with corresponding eigenvector $v + U \in V / U \setminus \{0\}$.
    From \exref{5b25} (a), we know that the minimal polynomial of $T$ is a multiple of the minimal polynomial of $T / U$.
    Since $\lambda$ is an eigenvalue of $T / U$, it must be a root of the minimal polynomial of $T / U$.
    Therefore, $\lambda$ is also a root of the minimal polynomial of $T$, which implies that $\lambda$ is an eigenvalue of $T$.
\end{sol}

\begin{exercise}[5b27]
    Suppose $\fbb = \rbb$, $V$ is finite-dimensional, and $T \in \lin{V}$.
	Prove that the minimal polynomial of $T_\cbb$ equals the minimal polynomial of $T$.

    \note{The complexification $T_\cbb$ was defined in \exref{3b33}.}
\end{exercise}

\begin{sol}
    Let $p(z)$ be the minimal polynomial of $T$.
    Then we have
    \[
    	p(T) = 0.
    \]
    Consider the complexification $T_\cbb$ of $T$.
    By definition, $T_\cbb$ applied on $v + iw \in V_\cbb$ is given by
    \[
    	T_\cbb(v + iw) = T(v) + iT(w)
    \]
    for all $v, w \in V$. By induction, we can extend the polynomial $p(z)$ to act on $V_\cbb$ by defining
    \[
    	p(T_\cbb)(v + iw) = p(T)v + ip(T)w.
    \]
    Since $p(T) = 0$, it follows that
    \[
    	p(T_\cbb)(v + iw) = 0 + i0 = 0
    \]
    for all $v, w \in V$.
    Therefore, $p(T_\cbb) = 0$, which shows that the minimal polynomial of $T_\cbb$ divides $p(z)$.

    Conversely, let $q(z)$ be the minimal polynomial of $T_\cbb$.
    We can split $q(z)$ into its real and imaginary parts, say $q(z) = r(z) + is(z)$, where $r(z), s(z) \in \pcal(\rbb)$.
    Then for any $v \in V$ which can be viewed as $v + i0 \in V_\cbb$, we have
    \[
    	q(T_\cbb)(v + i0) = r(T)(v + i0) + is(T)(v + i0) = r(T)v + i s(T)v.
    \]
    Since $q(T_\cbb) = 0$, it follows that $r(T)v = 0$ and $s(T)v = 0$ for all $v \in V$.
    Therefore, both $r(T)$ and $s(T)$ must be $0$, which implies that the minimal polynomial of $T$ divides $r(z)$ and $s(z)$.
    Since $q(z) = r(z) + is(z)$, it follows that the minimal polynomial of $T$ divides $q(z)$.
    Combining both directions, we conclude that the minimal polynomial of $T_\cbb$ equals the minimal polynomial of $T$.
\end{sol}

\begin{exercise}[5b28]
    Suppose $V$ is finite-dimensional and $T \in \lin{V}$.
	Prove that the minimal polynomial of $T' \in \lin{V'}$ equals the minimal polynomial of $T$.

    \note{The dual map $T'$ was defined in Section 3F, 3.118.}
\end{exercise}

\begin{sol}
    Let $p$ be the minimal polynomial of $T$. For any $\phi \in V'$, we have
    \[
    	p(T')(\phi)=\phi \circ p(T)=\phi \circ 0=0 \implies p(T')=0.
    \]
    Hence, the minimal polynomial of $T'$ divides $p$.

    Conversely, let $q$ be the minimal polynomial of $T'$, so $q(T')=0$. Then for all $\phi \in V'$ and all $v \in V$,
    \[
    	0=\left(q(T') \phi \right)(v)=\phi \left(q(T) v \right).
    \]
    Thus, for each fixed $v$, the functional $\phi$ is applied to $q(T)v$ gives zero for every $\phi \in V'$.
    Since $\phi(w) = 0$ for all $\phi \in V'$ implies $w = 0$, this forces $q(T)v=0$ for all $v$; i.e., $q(T)=0$. Therefore, $p$ divides $q$.

    Both $p$ and $q$ divide each other and are monic, so they are equal.
\end{sol}

\begin{exercise}[5b29]
    Show that every operator on a finite-dimensional vector space of dimension at least two has an invariant subspace of dimension two.

    \note{\emph{\exref{5c6}} will give an improvement of this result when $\fbb = \cbb$.}
    
    \apnote{5b29}{ for an alternate proof using upper-triangular matrices, which appear in the next section.}
\end{exercise}

\begin{sol}
    Let $V$ be a finite-dimensional vector space with $\dim V \geq 2$, and let $T \in \lin{V}$.
    Let $p(z)$ be the minimal polynomial of $T$.
    Over $\fbb$, every nonconstant polynomial factors into linear and irreducible quadratic factors.
    We split the proof into two cases based on the factorization of $p(z)$.
    \begin{enumerate}
        \item Suppose $p(z)$ has a linear factor $z - \lambda$ for some $\lambda \in \fbb$. 
        If $\deg p(z) = 1$, then $p(z) = z - \lambda$, which implies $T - \lambda I = 0$, or simply $T = \lambda I$. Since $T$ is just a scalar multiple of the identity, every single subspace of $V$ is invariant under $T$. Because $\dim V \geq 2$, we can choose any two linearly independent vectors $v, w \in V$, and $\spn(v, w)$ will form a 2-dimensional invariant subspace.

        If $\deg p(z) \geq 2$, then $p(z)/(z - \lambda)$ has degree at least 1 and must itself contain either a linear factor or an irreducible quadratic factor. The latter is handled by Case 2 below, so we consider the two linear cases:
        \begin{itemize}
            \item Repeated linear factor: $p(z) = (z - \lambda)^2 q(z)$.
            Since $p(z)$ is the minimal polynomial, there exists $v \in V$ such that $(T - \lambda I)q(T)v \neq 0$ but $(T - \lambda I)^2 q(T)v = 0$.
            Let $w = q(T)v$ and $u = (T - \lambda I)w$. 
            Then $u \neq 0$ and $(T - \lambda I)u = (T - \lambda I)^2 w = 0$, which implies $Tu = \lambda u$. 
            Thus, $u$ is an eigenvector corresponding to the eigenvalue $\lambda$. Moreover, $Tw = (T - \lambda I)w + \lambda w = u + \lambda w$, which shows that $Tw \in \spn(u, w)$. 
            
            To confirm linear independence, suppose $u = \alpha w$ for some $\alpha \in \fbb$.
            Then $(T - \lambda I)w = \alpha w$, so $w$ is an eigenvector of $T$ with eigenvalue $\lambda + \alpha$.
            But then $(T - \lambda I)^2 w = \alpha^2 w$. Since $(T - \lambda I)^2 w = 0$ and $w \neq 0$, this forces $\alpha = 0$, contradicting our deduction that $\alpha \neq 0$ (since $u \neq 0$).
            Therefore, $u$ and $w$ are linearly independent, and $\spn(u, w)$ is a 2-dimensional invariant subspace of $V$ under $T$.
            \item Distinct linear factor: $p(z) = (z - \lambda)(z - \mu)g(z)$ with $\lambda \neq \mu$.
            Then $T$ has two distinct eigenvalues, yielding two linearly independent eigenvectors $v$ and $u$.
            The subspace $\spn(v, u)$ is 2-dimensional, and since $Tv = \lambda v \in \spn(v, u)$ and $Tu = \mu u \in \spn(v, u)$, it is explicitly invariant.
        \end{itemize}

        \item Suppose $p(z)$ has an irreducible quadratic factor, say $z^2 + az + b$ for some $a, b \in \fbb$.
        This means we can write $p(z) = (z^2 + az + b)q(z)$ for some polynomial $q(z)$.
        Since $p(z)$ is the minimal polynomial, $q(T)$ is not the zero operator, meaning there exists some vector $x \in V$ such that $q(T)x \neq 0$.
        
        Let $u_1 = q(T)x$.
        Evaluating the minimal polynomial identity gives:
        \[
        	0 = p(T)x = (T^2 + aT + bI)q(T)x = (T^2 + aT + bI)u_1.
        \]
        Rearranging this provides the operator relation $T^2 u_1 = -b u_1 - a u_2$, where we define $u_2 = Tu_1$.
        
        The vectors $u_1$ and $u_2$ must be linearly independent.
        If $Tu_1 = cu_1$ for some $c \in \fbb$, then $(T^2 + aT + bI)u_1 = (c^2 + ac + b)u_1 = 0$.
        Since $u_1 \neq 0$, this implies $c^2 + ac + b = 0$, meaning $c$ is a root of $z^2 + az + b$ over $\fbb$, contradicting its irreducibility.
        
        Let $U = \spn(u_1, u_2)$, which has dimension two.
        Checking the images of our basis elements under $T$ yields:
        \begin{align*}
            T(u_1) &= u_2 \in U \\
            T(u_2) &= T^2 u_1 = -b u_1 - a u_2 \in U.
        \end{align*}
        Since $T$ maps the generating elements of $U$ back into $U$, the subspace $U$ is a 2-dimensional invariant subspace of $V$ under $T$.
    \end{enumerate}
\end{sol}