\subsection{Subspaces}

\begin{exercise}[1c1]
    For each of the following subsets of $\f^3$, determine whether it is a subspace of $\f^3$.
    \begin{subexercises}
        \item $\set{(x_1, x_2, x_3) \in \f^3 \mid x_1 + 2x_2 + 3x_3 = 0}$
        \item $\set{(x_1, x_2, x_3) \in \f^3 \mid x_1 + 2x_2 + 3x_3 = 4}$
        \item $\set{(x_1, x_2, x_3) \in \f^3 \mid x_1x_2x_3 = 0}$
        \item $\set{(x_1, x_2, x_3) \in \f^3 \mid x_1 = 5x_3}$
    \end{subexercises}
\end{exercise}

\begin{sol}
    Let $U$ be the subset of $\f^3$ in question.
    \begin{subexercises}
        \item Since the zero vector $(0, 0, 0)$ satisfies $0 + 2(0) + 3(0) = 0$, $U$ is nonempty. Let $u = (u_1, u_2, u_3)$ and $v = (v_1, v_2, v_3)$ be elements of $U$. Then
        \[(u_1 + v_1) + 2(u_2 + v_2) + 3(u_3 + v_3) = (u_1 + 2u_2 + 3u_3) + (v_1 + 2v_2 + 3v_3) = 0 + 0 = 0.\]
        Hence, $u + v$ is in $U$. Let $a \in \f$. Then
        \[a u_1 + 2(a u_2) + 3(a u_3) = a(u_1 + 2u_2 + 3u_3) = a \cdot 0 = 0.\]
        Hence, $au$ is in $U$. Therefore, $U$ is a subspace of $\f^3$.
        \item The zero vector $(0, 0, 0)$ does not satisfy $0 + 2(0) + 3(0) = 4$, so $U$ does not contain the zero vector. Hence, it is not a subspace of $\f^3$.
        \item Suppose $u = (1, 0, 0)$ and $v = (0, 1, 1)$. Then $u$ and $v$ are in $U$ since $1 \cdot 0 \cdot 0 = 0$ and $0 \cdot 1 \cdot 1 = 0$. However, $u + v = (1, 1, 1)$ is not in $U$ since $1 \cdot 1 \cdot 1 = 1 \neq 0$. Hence, $U$ is not closed under addition and is not a subspace of $\f^3$.
        \item Since the zero vector $(0, 0, 0)$ satisfies $0 = 5(0)$, $U$ is nonempty. Let $u = (u_1, u_2, u_3)$ and $v = (v_1, v_2, v_3)$ be elements of $U$. Then
        \[u_1 + v_1 = 5u_3 + 5v_3 = 5(u_3 + v_3).\]
        Hence, $u + v$ is in $U$. Let $a \in \f$. Then
        \[a u_1 = a(5u_3) = 5(a u_3).\]
        Hence, $au$ is in $U$. Therefore, $U$ is a subspace of $\f^3$. \qh
    \end{subexercises}
\end{sol}

\begin{exercise}[1c2]
    Verify all assertions about subspaces in Example 1.35.
    \begin{subexercises}
        \item If $b \in \f$, then
        \[\set{(x_1, x_2, x_3, x_4) \in \f^4 \mid x_3 = 5x_4 + b}\]
        is a subspace of $\f^4$ if and only if $b = 0$.
        \item The set of continuous, real-valued functions on the interval $[0, 1]$ is a subspace of $\r^{[0, 1]}$.
        \item The set of differentiable real-valued functions on $\r$ is a subspace of $\r^{\r}$.
        \item The set of differentiable real-valued functions $f$ on the interval $(0, 3)$ such that $f'(2) = b$ is a subspace of $\r^{(0, 3)}$ if and only if $b = 0$.
        \item The set of all sequences of complex numbers with limit 0 is a subspace of $\c^\infty$.
    \end{subexercises}
\end{exercise}

\begin{sol}
    Let $U$ be the subset of $\f^4$ in question.
    \begin{subexercises}
        \item Suppose $U$ is a subspace of $\f^4$. Then it must contain the zero vector $(0, 0, 0, 0)$. Then $0 = 5(0) + b$, which implies $b = 0$.
        
        Conversely, suppose $b = 0$. Then $U = \set{(x_1, x_2, x_3, x_4) \in \f^4 \mid x_3 = 5x_4}$. The proof is similar to that of \autoref{ex:1c1} (d), hence $U$ is a subspace of $\f^4$.
        \item Note that the 0 function on $[0, 1]$ is continuous, so $0 \in U$. Let $f, g \in U$ be continuous functions. Then $f + g$ is continuous, so $f + g \in U$. Let $a \in \r$. Then $af$ is continuous, so $af \in U$. Therefore, $U$ is a subspace of $\r^{[0, 1]}$.
        \item Since the derivative of the 0 function is the 0 function, $0 \in U$. Let $f, g \in U$ be differentiable functions. Then $f + g$ is differentiable, so $f + g \in U$. Let $a \in \r$. Then $af$ is differentiable, so $af \in U$. Therefore, $U$ is a subspace of $\r^{\r}$.
        \item Suppose $U$ is a subspace of $\r^{(0, 3)}$. Then it must contain the 0 function on $(0, 3)$. Then $0' = 0 = b$, which implies $b = 0$.
        
        Conversely, suppose $b = 0$. Then $U = \set{f \in \r^{(0, 3)} \mid f'(2) = 0}$. Let $f, g \in U$ be differentiable functions such that $f'(2) = g'(2) = 0$. Then
        \[(f + g)'(2) = f'(2) + g'(2) = 0 + 0 = 0,\]
        so $f + g \in U$. Let $a \in \r$. Then
        \[(af)'(2) = a f'(2) = a \cdot 0 = 0,\]
        so $af \in U$. Therefore, $U$ is a subspace of $\r^{(0, 3)}$.
        \item Let $U$ be the set of all sequences of complex numbers with limit 0. Then the zero sequence is in $U$. Let $(z_n), (w_n) \in U$ be sequences with limit 0. Then
        \[\lim_{n \to \infty} (z_n + w_n) = \lim_{n \to \infty} z_n + \lim_{n \to \infty} w_n = 0 + 0 = 0,\]
        so $(z_n) + (w_n) \in U$. Let $a \in \c$. Then
        \[\lim_{n \to \infty} (a z_n) = a \lim_{n \to \infty} z_n = a \cdot 0 = 0,\]
        so $a(z_n) \in U$. Therefore, $U$ is a subspace of $\c^\infty$. \qh
    \end{subexercises}
\end{sol}

\begin{exercise}[1c3]
    Show that the set of differentiable real-valued functions $f$ on the interval $(-4, 4)$ such that $f'(-1) = 3f(2)$ is a subspace of $\r^{(-4, 4)}$.
\end{exercise}

\begin{sol}
    Let $U$ be the set in question. Then the zero function is in $U$ since $0'(-1) = 0 = 3 \cdot 0 = 3 \cdot 0(2)$. Let $f, g \in U$ be differentiable functions such that $f'(-1) = 3f(2)$ and $g'(-1) = 3g(2)$. Then
    \[(f + g)'(-1) = f'(-1) + g'(-1) = 3f(2) + 3g(2) = 3(f(2) + g(2)) = 3(f + g)(2),\]
    so $f + g \in U$. Let $a \in \r$. Then
    \[(af)'(-1) = a f'(-1) = a \cdot 3f(2) = 3(af)(2),\]
    so $af \in U$. Therefore, $U$ is a subspace of $\r^{(-4, 4)}$.
\end{sol}

\begin{exercise}[1c4]
    Suppose $b \in \r$. Show that the set of continuous real-valued functions $f$ on the interval $[0, 1]$ such that
    \[\int_0^1 f = b\]
    is a subspace of $\r^{[0, 1]}$ if and only if $b = 0$.
\end{exercise}

\begin{sol}
    Let $U$ be the set in question. Suppose $U$ is a subspace of $\r^{[0, 1]}$. Then it must contain the zero function on $[0, 1]$. Then
    \[\int_0^1 0 = 0 = b,\]
    which implies $b = 0$.

    Conversely, suppose $b = 0$. Then
    \[U = \set*{f \in \r^{[0, 1]}\left|~\int_0^1 f = 0\right.}.\]
    The zero function is in $U$ since $\int_0^1 0 = 0$. Let $f, g \in U$ be continuous functions such that $\int_0^1 f = \int_0^1 g = 0$. Then
    \[\int_0^1 (f + g) = \int_0^1 f + \int_0^1 g = 0 + 0 = 0,\]
    so $f + g \in U$. Let $a \in \r$. Then
    \[\int_0^1 (af) = a \int_0^1 f = a \cdot 0 = 0,\]
    so $af \in U$. Therefore, $U$ is a subspace of $\r^{[0, 1]}$.
\end{sol}

\begin{exercise}[1c5]
    Is $\r^2$ a subspace of the complex vector space $\c^2$?
\end{exercise}

\begin{sol}
    No, $\r^2$ is not a subspace of $\c^2$. Let $u = (1, 0) \in \r^2$ and $a = i \in \c$. Then $au = (i, 0) \notin \r^2$, so $\r^2$ is not closed under scalar multiplication and is not a subspace of $\c^2$.
\end{sol}

\begin{exercise}[1c6]
    \begin{subexercises}
        \item Is $\set{(a, b, c) \in \r^3 \mid a^3 = b^3}$ a subspace of $\r^3$?
        \item Is $\set{(a, b, c) \in \c^3 \mid a^3 = b^3}$ a subspace of $\c^3$?
    \end{subexercises}
    \remark{Here, I present an elementary argument that does not require the use of De Moivre's Theorem; rather, I arrive at the conclusion directly. However, readers who are familiar with it may find it easier to note that the complex number 1 has three cube roots of unity. Other readers may also use Vieta's formulas to arrive at the same polynomial in $\omega$ to obtain $1 + \omega = -\omega^2$.}
\end{exercise}

\begin{sol}
    Let $U$ be the subset in question.
    \begin{subexercises}
        \item Since the zero vector $(0, 0, 0)$ satisfies $0^3 = 0^3$, $U$ is nonempty. Let $x = (x_1, x_2, x_3)$ and $y = (y_1, y_2, y_3)$ be elements of $U$. Then $x_1^3 = x_2^3$ and $y_1^3 = y_2^3$ both imply that $x_1 = x_2$ and $y_1 = y_2$. Hence,
        \[(x_1 + y_1)^3 = (x_2 + y_2)^3,\]
        so $x + y \in U$. Let $a \in \r$. Then
        \[(ax_1)^3 = a^3 x_1^3 = a^3 x_2^3 = (ax_2)^3,\]
        so $ax \in U$. Therefore, $U$ is a subspace of $\r^3$.
        \item No, $U$ is not a subspace of $\c^3$. To see this, consider the cubic polynomial $x^3 - 1 = 0$. This polynomial has three distinct roots in $\c$ as follows:
        \[x^3 - 1 = (x - 1)(x^2 + x + 1) = 0\]
        Applying the quadratic formula to $x^2 + x + 1 = 0$, we get
        \[x = \frac{-1 \pm \sqrt{(-1)^2 - 4(1)(1)}}{2(1)} = \frac{-1 \pm i\sqrt{3}}{2}.\]
        Let
        \[\omega = \frac{-1 + i\sqrt{3}}{2}.\]
        Then $\omega^3 = 1$, and
        \[\omega^2 = \frac{-1 - i\sqrt{3}}{2}.\]
        Moreover, it is not hard to see that $\omega + \omega^2 = -1$. Let $u = (1, 1, 0)$ and $v = (\omega, 1, 0)$. Then $u, v \in U$ since $1^3 = 1^3$ and $\omega^3 = 1^3$. Then $u + v = (1 + \omega, 2, 0)$. However,
        \[(1 + \omega)^3 = 1 + 3\omega + 3\omega^2 + \omega^3 = 1 + 3(-1) + 1 = -1 \neq 2^3 = 8.\]
        Hence, $u + v \notin U$, so $U$ is not closed under addition and is not a subspace of $\c^3$. \qh
    \end{subexercises}
\end{sol}

\begin{exercise}[1c7]
    Prove or give a counterexample: If $U$ is a nonempty subset of $\r^2$ such that $U$ is closed under addition and under taking additive inverses (meaning $-u \in U$ whenever $u \in U$), then $U$ is a subspace of $\r^2$.
\end{exercise}

\begin{sol}
    Consider the subset $\q^2$ of $\r^2$. Then $\q^2$ is nonempty because $(0, 0) \in \q^2$, closed under addition since the sum of any two rational numbers is rational, and closed under taking additive inverses since the additive inverse of a rational number is rational. However, for any irrational number $r \in \r$, the vector $(r, 0) = r(1, 0) \in \r^2$ is not in $\q^2$. Hence, $\q^2$ is not closed under scalar multiplication and is not a subspace of $\r^2$. Therefore, the statement is false.
\end{sol}

\begin{exercise}[1c8]
    Give an example of a nonempty subset $U$ of $\r^2$ such that $U$ is closed under scalar multiplication, but $U$ is not a subspace of $\r^2$.
\end{exercise}

\begin{sol}
    Consider the subset
    \[U = \{(x, 0) \mid x \in \r\} \cup \{(0, y) \mid y \in \r\}.\]
    Then $U$ is nonempty since $(1, 0) \in U$, and it is closed under scalar multiplication since any scalar multiple of $(1, 0)$ or $(0, 1)$ is still in $U$. However, $U$ is not closed under addition since $(1, 0) + (0, 1) = (1, 1) \notin U$. Hence, $U$ is not a subspace of $\r^2$.
\end{sol}

\begin{exercise}[1c9]
    A function $f : \r \to \r$ is called \textbf{periodic} if there exists a positive number $p$ such that $f(x + p) = f(x)$ for all $x \in \r$. Is the set of periodic functions from $\r$ to $\r$ a subspace of $\r^{\r}$? Explain.
\end{exercise}

\begin{sol}
    It is not a subspace of $\r^{\r}$. Consider the periodic functions $f(x) = \cos x$ and $g(x) = \cos \sqrt 2x$. Then the sum $f + g$ attains a maximum value of 2 at 0. If $f + g$ were periodic with period $p$, then $(f + g)(p) = (f + g)(0) = 2$. This implies $\cos p = \cos p\sqrt 2 = 1$. Then $p = 2\pi m$ and $p\sqrt 2 = 2\pi n$ for positive integers $m$ and $n$. Since $p \sqrt 2 = 2 \pi n$ implies $p = \sqrt 2 \pi n$, we have
    \[2\pi m = \sqrt 2\pi n \implies \sqrt 2 = \frac nm,\]
    which is a contradiction, since $\sqrt 2$ is irrational. Then $f + g$ is not periodic.
\end{sol}

\begin{exercise}[1c10]
    Suppose $V_1$ and $V_2$ are subspaces of $V$. Prove that the intersection $V_1 \cap V_2$ is a subspace of $V$.
\end{exercise}

\begin{sol}
    Let $U = V_1 \cap V_2$. Since both $V_1$ and $V_2$ are subspaces of $V$, they both contain the zero vector of $V$. Hence, $0 \in U$, so $U$ is nonempty. Let $u, v \in U$. Then $u, v \in V_1$ and $u, v \in V_2$. Since both $V_1$ and $V_2$ are subspaces, they are closed under addition. Therefore, $u + v \in V_1$ and $u + v \in V_2$, which implies that $u + v \in U$. Let $a \in \f$. Then since both $V_1$ and $V_2$ are closed under scalar multiplication, we have that $au \in V_1$ and $au \in V_2$, which implies that $au \in U$. Therefore, $U$ is a subspace of $V$.
\end{sol}

\begin{exercise}[1c11]
    Prove that the intersection of every collection of subspaces of $V$ is a subspace of $V$.
\end{exercise}

\begin{sol}
    Let $\cc$ be a collection of subspaces of $V$, and let
    \[U = \bigcap_{W \in \cc} W.\]
    Since each subspace in $\cc$ contains the zero vector, $0 \in U$, so $U$ is nonempty. Let $u, v \in U$. Then $u, v \in W$ for all $W \in \cc$. Since each $W$ is a subspace, they are closed under addition, so $u + v \in W$ for all $W \in \cc$, which implies $u + v \in U$. Let $a \in \f$. Then $au \in W$ for all $W \in \cc$, which implies $au \in U$. Therefore, $U$ is a subspace of $V$.
\end{sol}

\begin{exercise}[1c12]
    Prove that the union of two subspaces of $V$ is a subspace of $V$ if and only if one of the subspaces is contained in the other.
\end{exercise}

\begin{sol}
    Let $U, W$ be subspaces of $V$. Suppose $U \subseteq W$. Then $U \cup W = W$, which is a subspace of $V$. Similarly, if $W \subseteq U$, then $U \cup W = U$, which is a subspace of $V$.

    Conversely, suppose $U \cup W$ is a subspace of $V$. If neither $U \subseteq W$ nor $W \subseteq U$, then there exist $u \in U \setminus W$ and $w \in W \setminus U$. Since $U \cup W$ is a subspace, it must be closed under addition. Then $u + w \in U \cup W$. However, $u + w \notin U$ because if it were, then $w = (u + w) - u \in U$, which is a contradiction. Similarly, $u + w \notin W$ because if it were, then $u = (u + w) - w \in W$, which is also a contradiction. Hence, $u + w \notin U \cup W$, which contradicts the assumption that $U \cup W$ is a subspace. Therefore, one of the subspaces must be contained in the other.
\end{sol}

\begin{exercise}[1c13]
    Prove that the union of three subspaces of $V$ is a subspace of $V$ if and only if one of the subspaces contains the other two.

    \note{This result fails when the field has only two elements.}

    \remark{The proof of this exercise is more involved than the proof of \emph{\autoref{ex:1c12}} in that it requires a more careful analysis of the possible relationships between the three subspaces.}

    \apnote{1c13}{ for a more elegant proof of this result, which implicitly uses the result that $\cha(\f) \neq 2$.}
\end{exercise}

\begin{sol}
    Let $U_1, U_2, U_3$ be subspaces of $V$. Without loss of generality, suppose $U_2 \subseteq U_1$ and $U_3 \subseteq U_1$. Then $U_1 \cup U_2 \cup U_3 = U_1$, which is a subspace of $V$.

    Conversely, suppose $U_1 \cup U_2 \cup U_3$ is a subspace of $V$. Suppose that some pair satisfies containment, say $U_3 \subseteq U_2$. Let $W = U_2 \cup U_3 = U_2$. Then $U_1 \cup W = U_1 \cup U_2 \cup U_3$. By \autoref{ex:1c12}, either $U_1 \subseteq U_2$ or $U_2 \subseteq U_1$. If the former occurs, then $U_1 \cup U_2 = U_2$, which contains $U_3$. If the latter occurs, then $U_1 \cup U_2 = U_1$. Since $U_3 \subseteq U_2$, then $U_3 \subseteq U_1$. Therefore, one of the subspaces must contain the other two.

    Now suppose no subspace is contained in another. Then there exist $u \in U_2 \setminus U_3$ and $v \in U_3 \setminus U_2$. Since $U_1 \cup U_2 \cup U_3$ is a subspace, $u + \alpha v \in U_1 \cup U_2 \cup U_3$ for any nonzero $\alpha \in \f$. If $u + \alpha v \in U_2$, then $\alpha v = (u + \alpha v) - u \in U_2$, which implies $v \in U_2$, a contradiction. If $u + \alpha v \in U_3$, then $u = (u + \alpha v) - \alpha v \in U_3$, a contradiction. Then $u + \alpha v \in U_1$ for all nonzero $\alpha \in \f$. Now choose nonzero $\beta, \gamma \in \f$ with $\beta \neq \gamma$. Then $u + \beta v, u + \gamma v \in U_1$, so
    \[(u + \beta v) - (u + \gamma v) = (\beta - \gamma)v \in U_1.\]
    Since $\beta - \gamma \neq 0$, we have $v \in U_1$. Similarly, $(u + \beta v) - \beta v = u \in U_1$. Since $u \in U_2 \setminus U_3$ and $v \in U_3 \setminus U_2$ were arbitrary, $U_2 \setminus U_3 \subseteq U_1$ and $U_3 \setminus U_2 \subseteq U_1$.

    Now let $w \in U_2 \cap U_3$. Since $U_2 \nsubseteq U_3$, there exists $x \in U_2 \setminus U_3 \subseteq U_1$. Then $w + x \in U_2$. If $w + x \in U_3$, then $x = (w + x) - w \in U_3$, a contradiction. Hence, $w + x \in U_2 \setminus U_3 \subseteq U_1$, so $w = (w + x) - x \in U_1$. Therefore, $U_2 \cap U_3 \subseteq U_1$, which gives $U_2 = (U_2 \setminus U_3) \cup (U_2 \cap U_3) \subseteq U_1$ and similarly $U_3 \subseteq U_1$, contradicting our assumption. Hence, one of the subspaces must contain the other two.
\end{sol}

\begin{exercise}[1c14]
    Suppose
    \[U = \set{(x, -x, 2x) \in \f^3 \mid x \in \f} \quad \text{and} \quad W = \set{(x, x, 2x) \in \f^3 \mid x \in \f}.\]
    Describe $U + W$ using symbols, and also give a description of $U + W$ that uses no symbols.
\end{exercise}

\begin{sol}
    Let $u = (x, -x, 2x) \in U$ and $w = (y, y, 2y) \in W$. Then
    \[u + w = (x + y, -x + y, 2x + 2y) = (x + y, y - x, 2(x + y)).\]
    Observe that $x + y$ can take any value in $\f$, and $y - x$ can also take any value in $\f$. Hence, we can write
    \[U + W = \set{(a, b, 2a) \in \f^3 \mid a, b \in \f}.\]
    In words, $U + W$ is the set of all vectors in $\f^3$ whose third component is twice the first component, and whose second component can be any value in $\f$.
\end{sol}

\begin{exercise}[1c15]
    Suppose $U$ is a subspace of $V$. What is $U + U$?
\end{exercise}

\begin{sol}
    Let $u_1, u_2 \in U$. Then $u_1 + u_2 \in U$ since $U$ is closed under addition. Hence, $U + U \subseteq U$. Conversely, let $u \in U$. Then $u = u + 0$, where $0$ is the additive identity in $U$. Since $0 \in U$, we have that $u \in U + U$. Hence, $U \subseteq U + U$. Therefore, $U + U = U$.
\end{sol}

\begin{exercise}[1c16]
    Is the operation of addition on subspaces of $V$ commutative? In other words, if $U$ and $W$ are subspaces of $V$, is $U + W = W + U$?
\end{exercise}

\begin{sol}
    Yes, the operation of addition on subspaces of $V$ is commutative. Let $u \in U$ and $w \in W$. Then $u + w \in U + W$. Because addition in $V$ is commutative, we have that $u + w = w + u$, where $w \in W$ and $u \in U$. Hence, $w + u \in W + U$. Therefore, every element of $U + W$ is also an element of $W + U$, which implies that $U + W \subseteq W + U$. By a similar argument, we can show that $W + U \subseteq U + W$. Hence, $U + W = W + U$.
\end{sol}

\begin{exercise}[1c17]
    Is the operation of addition on the subspaces of $V$ associative? In other words, if $V_1, V_2, V_3$ are subspaces of $V$, is
    \[(V_1 + V_2) + V_3 = V_1 + (V_2 + V_3)?\]
\end{exercise}

\begin{sol}
    Yes, the operation of addition on subspaces of $V$ is associative. Let $u_1 \in V_1$, $u_2 \in V_2$, and $u_3 \in V_3$. Then $(u_1 + u_2) + u_3 \in (V_1 + V_2) + V_3$. Because addition in $V$ is associative, we have that $(u_1 + u_2) + u_3 = u_1 + (u_2 + u_3)$, where $u_1 \in V_1$, $u_2 \in V_2$, and $u_3 \in V_3$. Hence, $u_1 + (u_2 + u_3) \in V_1 + (V_2 + V_3)$. Therefore, every element of $(V_1 + V_2) + V_3$ is also an element of $V_1 + (V_2 + V_3)$, which implies that $(V_1 + V_2) + V_3 \subseteq V_1 + (V_2 + V_3)$. By a similar argument, we can show that $V_1 + (V_2 + V_3) \subseteq (V_1 + V_2) + V_3$. Hence, $(V_1 + V_2) + V_3 = V_1 + (V_2 + V_3)$.
\end{sol}

\begin{exercise}[1c18]
    Does the operation of addition on the subspaces of $V$ have an additive identity? Which subspaces have additive inverses?
\end{exercise}

\begin{sol}
    Yes, the operation of addition on the subspaces of $V$ has an additive identity. The additive identity is the zero subspace $\{0\}$, which contains only the zero vector of $V$. For any subspace $U$ of $V$, we have that $U + \{0\} = U$.

    If a subspace $U$ of $V$ had an additive inverse $W$, then we would have that $U + W = \{0\}$. However, $U \subseteq U + W$ since $u = u + 0$ for any $u \in U$. Hence, $U + W = \{0\}$ implies that $U = \{0\}$. Therefore, the only subspace of $V$ that has an additive inverse is the zero subspace $\{0\}$.
\end{sol}

\begin{exercise}[1c19]
    Prove or give a counterexample: If $V_1, V_2, U$ are subspaces of $V$ such that
    \[V_1 + U = V_2 + U,\]
    then $V_1 = V_2$.
\end{exercise}

\begin{sol}
    The statement is false. Consider the vector space $\r^2$ and let
    \[V_1 = \set{(x, 0) \in \r^2 \mid x \in \r}, \quad V_2 = \set{(0, y) \in \r^2 \mid y \in \r}, \quad U = \set{(x, x) \in \r^2 \mid x \in \r}.\]
    Then $V_1 + U = \r^2$ and $V_2 + U = \r^2$, but $V_1 \neq V_2$. Therefore, the statement is false.
\end{sol}

\begin{exercise}[1c20]
    Suppose
    \[U = \set{(x, x, y, y) \in \f^4 \mid x, y \in \f}.\]
    Find a subspace $W$ of $\f^4$ such that $\f^4 = U \op W$.
\end{exercise}

\begin{sol}
    Let
    \[W = \set{(0, z, 0, w) \in \f^4 \mid z, w \in \f}.\]
    If $(x, x, y, y) \in U$ and $(0, z, 0, w) \in W$, then $(x, x, y, y) = (0, z, 0, w)$ if and only if $x = 0$, $y = 0$, $z = 0$, and $w = 0$. Hence, $U \cap W = \{0\}$. Moreover, for any $(a, b, c, d) \in \f^4$, we can write
    \[(a, b, c, d) = (x, x, y, y) + (0, z, 0, w),\]
    where
    \[x = a, \quad y = c, \quad z = b - x = b - a, \quad w = d - y = d - c.\]
    Hence, every vector in $\f^4$ can be written as a sum of a vector in $U$ and a vector in $W$. Therefore, $\f^4 = U \op W$.
\end{sol}

\begin{exercise}[1c21]
    Suppose
    \[U = \set{(x, y, x + y, x - y, 2x) \in \f^5 \mid x, y \in \f}.\]
    Find a subspace $W$ of $\f^5$ such that $\f^5 = U \op W$.
\end{exercise}

\begin{sol}
    Let
    \[W = \set{(0, 0, z, w, v) \in \f^5 \mid z, w, v \in \f}.\]
    If $(x, y, x + y, x - y, 2x) \in U$ and $(0, 0, z, w, v) \in W$, then $(x, y, x + y, x - y, 2x) = (0, 0, z, w, v)$ if and only if $x = 0$, $y = 0$, $z = 0$, $w = 0$, and $v = 0$. Hence, $U \cap W = \{0\}$. Moreover, for any $(a, b, c, d, e) \in \f^5$, we can write
    \[(a, b, c, d, e) = (x, y, x + y, x - y, 2x) + (0, 0, z, w, v),\]
    which implies
    \[
    \begin{cases}
        a = x + 0 \\
        b = y + 0 \\
        c = (x + y) + z \\
        d = (x - y) + w \\
        e = 2x + v
    \end{cases} \implies 
    \begin{cases}
        x = a \\
        y = b \\
        z = c - (x + y) = c - (a + b) \\
        w = d - (x - y) = d - (a - b) \\
        v = e - 2x = e - 2a
    \end{cases}\]
    Hence, every vector in $\f^5$ can be written as a sum of a vector in $U$ and a vector in $W$. Therefore, $\f^5 = U \op W$.
\end{sol}

\begin{exercise}[1c22]
    Suppose
    \[U = \set{(x, y, x + y, x - y, 2x) \in \f^5 \mid x, y \in \f}.\]
    Find three subspaces $W_1, W_2, W_3$ of $\f^5$, none of which equals $\set 0$, such that $\f^5 = U \op W_1 \op W_2 \op W_3$.

    \remark{The derivation of $z, w, e$ is from \emph{\autoref{ex:1c21}}.}
\end{exercise}

\begin{sol}
    Observe that $U$ can be expressed as
    \[U = \set{(x, 0, x, x, 2x) \in \f^5 \mid x \in \f} + \set{(0, y, y, -y, 0) \in \f^5 \mid y \in \f}.\]
    Define the subspaces
    \begin{align*}
        W_1 &= \set{(0, 0, z, 0, 0) \in \f^5 \mid z \in \f}, \\
        W_2 &= \set{(0, 0, 0, w, 0) \in \f^5 \mid w \in \f}, \\
        W_3 &= \set{(0, 0, 0, 0, v) \in \f^5 \mid v \in \f}.
    \end{align*}
    Consider $(a, b, c, d, e) \in \f^5$. We can write
    \[(a, b, c, d, e) = (x, 0, x, x, 2x) + (0, y, y, -y, 0) + (0, 0, z, 0, 0) + (0, 0, 0, w, 0) + (0, 0, 0, 0, v),\]
    where
    \begin{align*}
        x &= a, \\
        y &= b, \\
        z &= c - a - b, \\
        w &= d - a + b, \\
        v &= e - 2a.
    \end{align*}
    Hence, every vector in $\f^5$ can be written as a sum of a vector in $U$ and vectors in $W_1, W_2, W_3$. Moreover, if $a = b = c = d = e = 0$, then $x = y = z = w = v = 0$ so that the only way to write the zero vector as a sum of vectors in $U, W_1, W_2, W_3$ is to take all of them to be the zero vector. Therefore, $\f^5 = U \op W_1 \op W_2 \op W_3$.
\end{sol}

\begin{exercise}[1c23]
    Prove or give a counterexample: If $V_1, V_2, U$ are subspaces of $V$ such that
    \[V = V_1 \op U \quad \text{ and } \quad V = V_2 \op U,\]
    then $V_1 = V_2$.
\end{exercise}

\begin{sol}
    See \autoref{ex:1c19} for a counterexample. For $V_1 \op U$, observe that $V_1 \cap U = \set 0$. Moreover, for any $(a, b) \in \r^2$, we can write
    \[(a, b) = (a - b, 0) + (b, b) \in V_1 \op U.\]
    The proof for $V_2 \op U$ is similar. Hence, $V = V_1 \op U = V_2 \op U$, but $V_1 \neq V_2$. Therefore, the statement is false.
\end{sol}

\begin{exercise}[1c24]
    A function $f : \r \to \r$ is called \textbf{even} if
    \[f(-x) = f(x)\]
    for all $x \in \r$. A function $f : \r \to \r$ is called \textbf{odd} if
    \[f(-x) = -f(x)\]
    for all $x \in \r$. Let $V_e$ denote the set of real-valued even functions on $\r$, and let $V_o$ denote the set of real-valued odd functions on $\r$. Show that $\r^{\r} = V_e \op V_o$.
\end{exercise}

\begin{sol}
    Let $f \in \r^{\r}$. Define
    \[f_e(x) = \frac{f(x) + f(-x)}{2} \quad \text{and} \quad f_o(x) = \frac{f(x) - f(-x)}{2}.\]
    Then $f_e$ is even since
    \[f_e(-x) = \frac{f(-x) + f(x)}{2} = f_e(x),\]
    and $f_o$ is odd since
    \[f_o(-x) = \frac{f(-x) - f(x)}{2} = -\frac{f(x) - f(-x)}{2} = -f_o(x).\]
    Moreover, we have that
    \[f(x) = f_e(x) + f_o(x).\]
    Hence, every function in $\r^{\r}$ can be written as a sum of an even function and an odd function. 

    Now, suppose $g \in V_e \cap V_o$. Then $g$ is both even and odd. Then for any $x \in \r$, we have
    \[g(x) = g(-(-x)) = -g(-x) = -g(x),\]
    which implies that $2g(x) = 0$, or $g(x) = 0$. Hence, the only function in the intersection of $V_e$ and $V_o$ is the zero function. Therefore, $\r^{\r} = V_e \op V_o$.
\end{sol}