\subsection{Linear Maps}

\begin{apex}[3b29]
    Suppose $p \in \pcal(\rbb)$.
	Prove that there exists a polynomial $q \in \pcal(\rbb)$ such that $5q'' + 3q' = p$.
\end{apex}

\begin{coole}
    Let $p(x) = a_0 + a_1x + \cdots + a_nx^n$ and suppose there exists a polynomial $q(x) = b_0 + b_1x + \cdots + b_mx^m$ satisfying $5q'' + 3q' = p$. 
    If $\deg q = m \geq 2$, we can say $q'$ has degree $m-1$ and $q''$ has degree $m-2$, so $5q'' + 3q'$ has degree $m-1$.
    To satisfy the given equation, then, we must have $m-1 = n = \deg p$, and we may write $q(x) = b_0 + b_1x + \cdots + b_{n+1}x^{n+1}$.
    Before we deal with the general case, we will quickly consider when $n = 0$ (which would force $m < 2$):

    If $p(x) = a_0$, then let $q(x) = b_0 + b_1x$. Because $5q'' + 3q' = p$, we have $5q'' + 3q' = 5(0) + 3b_1 = a_0$, so we set $b_1 = \frac{a_0}{3}$ and we have a polynomial $q$ such that $5q'' + 3q' = p$ for any value of $b_0$.
    As we will see below, the constant term of $q$ never depends on $p$.
    
    For the remainder of this proof, we take $m = n+1$ and suppose $n \geq 1$.
    We have
    \begin{align*}
        q'(x) &= b_1 + 2b_2x + \cdots + (n+1)b_{n+1}x^n \\
        q''(x) &= 2b_2 + 6b_3x + \cdots + n(n+1)b_{n+1}x^{n-1}
    \end{align*}
    Equating coefficients of $5q'' + 3q'$ with those of $p$, we obtain the system
    \[
    \begin{cases}
        a_0 = 3b_1 + 10b_2 \\
        a_1 = 6b_2 + 30b_3 \\
        \vdots \\ 
        a_{n-1} = 3nb_n + 5n(n+1)b_{n+1} \\
        a_n = 3(n+1)b_{n+1}
    \end{cases}.\]
    That is, $a_i = 3(i+1)b_{i+1} + 5(i+1)(i+2)b_{i+2}$ for $0 \leq i < n$ and $a_n = 3(n+1)b_{n+1}$.
    Finally, we solve for the coefficients of $q$ by back-substitution.
    Noting that
    \[b_j = \frac{a_{j-1} - 5j(j+1)b_{j+1}}{3j} = \frac{a_{j-1}}{3j} - \frac{5}{3}(j+1)b_{j+1},\] we have 
    \[\begin{cases}
        b_{n+1} = \frac{a_n}{3(n+1)} \\
        b_n = \frac{a_{n-1}}{3n} - \frac{5}{3}(n+1)b_{n+1} = \frac{a_{n-1}}{3n} - \frac{5}{9}a_n \\
        b_{n-1} = \frac{a_{n-2}}{3(n-1)} - \frac{5}{3}nb_n = \frac{a_{n-2}}{3(n-1)} - \frac{5}{9}a_{n-1} + \frac{25}{27}na_n \\
        \vdots \\
        b_1 = \frac{a_0 - 10b_2}{3}
    \end{cases}\]
    which has a valid solution$^\dagger$ since no division by $0$ occurs.
    Finally, we note that $b_0$ is a free variable, so there is an infinite family of polynomials $q \in \pcal(\rbb)$ with the given coefficients such that $5q'' + 3q' = p$. 
\end{coole}
$^\dagger$ Solving this recurrence is outside the scope of this course, but, specifically, the coefficients of $q$ are 
\begin{align*}
    b_j &= \frac{a_{j-1}}{3j} - \frac{5}{9}a_j + \frac{25}{27}(j+1)a_{j+1} - \frac{125}{81}(j+1)(j+2)a_{j+2} + \cdots + (-1)^{n-j+1}\frac{5^{n-j+1}}{3^{n-j+2}}(j+1)(j+2)\cdots na_n \\
    &= \frac{1}{3}\left(\frac{a_{j-1}}{j} + \sum_{i=j}^n\left(-\frac{5}{3}\right)^{i-j+1}\frac{i!}{j!}a_{i}\right).
\end{align*}

\begin{apex}[3d19]
    Suppose $V$ is finite-dimensional and $T \in \lin{V}$.
	Prove that $T$ has the same matrix with respect to every basis of $V$ if and only if $T$ is a scalar multiple of the identity operator.
\end{apex}

The manual solution provides a constructive proof utilizing sums of the form $v_1 + v_k$ to eliminate the $k$-th column, along with $v_2 + v_1$ to eliminate the 1st column.
Here, we present different constructions.
Each proof assumes the declaration of the matrix to be $A$ and that $\dim V \geq 2$.

This method shows that we can swap two \emph{arbitrary} basis vectors to force the same value of all off-diagonal entries as well as the same value of all diagonal entries.
Then, we can negate one basis vector to force all off-diagonal entries to be 0 via the linear independence of the basis vectors.

\begin{coole}
    Let $i,j$ be arbitrary with $1 \leq i,j \leq n$ and $i \neq j$.
    Consider the basis $w_1, \dots, w_n$ of $V$ defined by $w_i = v_j$, $w_j = v_i$ and $w_k = v_k$ otherwise.
    Then 
    \begin{align*}
        T(w_j - v_i) &= Tw_j - Tv_i \\
        T(0) &= A_{1,j}w_1 + A_{2,j}w_2 + \cdots + A_{n,j}w_n - (A_{1,i}v_1 + A_{2,i}v_2 + \cdots + A_{n,i}v_n) \\
        0 &= (A_{j,j} - A_{i,i})v_i + (A_{i,j} - A_{j,i})v_j + \sum_{\substack{k \neq i \\ k \neq j}}(A_{k,j} - A_{k,i})v_k.
    \end{align*}
    By linear independence of $v_1, \dots, v_n$, we have $A_{i,i} = A_{j,j}$, $A_{i,j} = A_{j,i}$ and $A_{k,j} = A_{k,i}$ for all $k \neq i,j$.
    Because $i$ and $j$ were arbitrary, we have $A_{1,1} = A_{2,2} = \cdots = A_{n,n} = \lambda$, as well as $A$ is symmetric, and all off-diagonal entries match across rows, so we can say $A_{i,j} = \gamma$ for all $i \neq j$.
    To finish, consider the basis $u_1, \dots, u_n$ defined by $u_1 = -v_1$ and $u_k = v_k$ otherwise.
    Then 
    \begin{align*}
        T(v_1 + u_1) &= Tv_1 + Tu_1 \\
        T(0) &= \lambda v_1 + \gamma(v_2 + \cdots + v_n) + (\lambda u_1 + \gamma(u_2 + \cdots + u_n)) \\
        0 &= 2\gamma(v_2 + \cdots + v_n).
    \end{align*}
    Again by linear independence of $v_1, \dots, v_n$, we have $2\gamma = 0$ and thus $\gamma = 0$.
    Therefore, $A = \lambda I$ and $T$ is a scalar multiple of the identity.
\end{coole}

This method shows that we can negate one \emph{arbitrary} basis vector to force all off-diagonal entries to be 0 via the linear independence of the basis vectors.
Then, we can swap $v_1$ with any other basis vector to force all diagonal entries to be the same.

\begin{coole}
    Let $j$ be arbitrary and consider the basis $w_1, \dots, w_n$ of $V$ defined by $w_j = -v_j$ and $w_i = v_i$ otherwise.
	Then
    \begin{align*}
        T(w_j + v_j) &= Tw_j + Tv_j \\
        T(0) &= A_{1,j}w_1 + A_{2,j}w_2 + \cdots + A_{n,j}w_n + A_{1,j}v_1 + A_{2,j}v_2 + \cdots + A_{n,j}v_n \\
        0 &= 2\sum_{k \neq j}A_{k,j}v_k.
    \end{align*}
    By linear independence of $v_1, \dots, v_n$, we have $A_{k,j} = 0$ for all $k \neq j$.
	Since $j$ was arbitrary, we have that all off-diagonal entries of $A$ are 0.

    We turn to one more basis to prove that all diagonal entries of $A$ must be the same.
	Once again, let $j$ be arbitrary, and this time consider the basis $u_1, \dots, u_n$ defined by $u_1 = v_j$, $u_j = v_1$ and $u_i = v_i$ otherwise.
	Then
    \begin{align*}
        T(v_1 - u_j) &= Tv_1 - Tu_j \\
        T(0) &= A_{1,1}v_1 - A_{j,j}u_j \\
        0 &= (A_{1,1} - A_{j,j})v_1.
    \end{align*}
    As $v_1$ belongs to a basis for $V$, it is nonzero, and thus as $j$ was arbitrary, $A_{1,1} = A_{2,2} = \cdots = A_{n,n} = \lambda$ for some scalar $\lambda$, and we have $A = \lambda I$, i.e., $T$ is a multiple of the identity operator.
\end{coole}

\begin{apex}[3e11]
    Suppose $U = \set{(x_1, x_2, \ldots) \in \fbb^\infty \mid x_k \neq 0 \text{ for only finitely many } k}$.
    \begin{subexercises}
        \item Show that $U$ is a subspace of $\fbb^\infty$.
        \item Prove that $\fbb^\infty / U$ is infinite-dimensional.
    \end{subexercises}
\end{apex}

\begin{proof}
    \leavevmode
    \begin{subexercises}
        \item Since $(0,0,\dots) \in U$, $U$ is nonempty.
	Suppose $x$, $y \in U$ and $c \in \mathbb{F}$.
	Let $S_x$ and $S_y$ be the sets of indices where $x$ and $y$ have nonzero terms, respectively.
	By definition, $S_x$ and $S_y$ are finite. $cx+y$ can only have nonzero terms at indices in $S_x \cup S_y$.
	Since the union of two finite sets is finite, $cx+y \in U$, which makes $U$ a subspace of $\mathbb{F}^{\infty}$. 

        \item Partition $\mathbb{Z}^{+}$ into a countably infinite family of disjoint infinite subsets $A_1$, $A_2$, $\dots$.
	For each $n$, define $v_n \in \mathbb{F}^{\infty}$ such that its $j$-th term is $1$ if $j \in A_n$ and $0$ otherwise.

        Suppose that $\sum^{m}_{i=1} c_i (v_i+U)=0+U$ for some positive integer $m$ and scalars $c_1$, $\dots$, $c_m \in \mathbb{F}$.
	Then, $w=\sum^{m}_{i=1} c_i v_i \in U$.
	By construction, for $i \in \{1, \dots, m\}$, the $j$-th term of $w$ is $c_i$ for all $j \in A_i$.
	Since $w \in U$, it only has a finite number of nonzero terms.
	But each $A_i$ is infinite, so this forces $c_i=0$ for all $i \in \{1, \dots, m\}$.
	Hence, $v_1+U$, $v_2+U$, $\dots$ are linearly independent in $\mathbb{F}^{\infty}/U$.

        Because $\mathbb{F}^{\infty}/U$ contains an infinite sequence of linearly independent vectors, it is infinite-dimensional.
    \end{subexercises}
\end{proof}

\begin{apex}[3f11]
    Suppose $v_1, \ldots, v_n$ is a basis of $V$ and $\phi_1, \ldots, \phi_n$ is the corresponding dual basis of $V'$.
	Suppose $\psi \in V'$.
	Prove that
    \[\psi = \psi(v_1) \phi_1 + \cdots + \psi(v_n) \phi_n.\]
\end{apex}

\begin{csp}
    Because $\phi_1$, $\dots$, $\phi_n$ is the dual basis, $\phi_i (v_j)=\delta_{i,j}$.
	For each basis vector $v_j$,
    $$\left(\sum^{n}_{i=1} \psi(v_i) \phi_i \right)(v_j)=\sum^{n}_{i=1} \psi(v_i) \phi_i (v_j)=\psi(v_j).$$
    Since the two linear functionals agree on a basis of $V$, they are equal on all of $V$.
\end{csp}