\setcounter{subsection}{4}

\subsection{Eigenvalues and Eigenvectors}

\begin{exercise}[5a27]
    Suppose that $V$ is finite-dimensional and $k \in \{1, \ldots, \dim V - 1\}$.
	Suppose $T \in \lin{V}$ is such that every subspace of $V$ of dimension $k$ is invariant under $T$.
	Prove that $T$ is a scalar multiple of the identity operator.
\end{exercise}

\begin{csp}
    Let $v \in V$ be nonzero. For any $u \notin \operatorname{span}(v)$, we can extend $v$, $u$ to a basis and construct a $k$-dimensional subspace that contains $v$ but not $u$ since $k \in \{1, \dots, \dim V-1\}$. So, the intersection of all $k$-dimensional subspaces containing $v$ is precisely $\operatorname{span}(v)$. \\ 

    The intersection of invariant subspaces is invariant, so $\operatorname{span}(v)$ is invariant. This means that every nonzero vector is an eigenvector of $T$, meaning that $T$ is a scalar multiple of the identity by \exref{5a26}.
\end{csp}

\begin{apex}[5a42]
    Define $T \in \lin{\fbb^n}$ by $T(x_1, x_2, x_3, \ldots, x_n) = (x_1, 2x_2, 3x_3, \ldots, nx_n)$.
    \begin{subexercises}
        \item Find all eigenvalues and eigenvectors of $T$.
        \item Find all subspaces of $\fbb^n$ that are invariant under $T$.
    \end{subexercises}
\end{apex}

\begin{csp}
    Let $e_1$, $\dots$, $e_n$ be the standard basis of $\mathbb{F}^n$.
    \begin{subexercises}
        \item For each $k \in \{1, \dots, n\}$, we have $Te_k=ke_k$.
		Hence, the eigenvalues of $T$ are $1$, $2$, $\dots$, $n$ and the eigenvectors corresponding to $k$ are the nonzero scalar multiples of $e_k$.
		Note that this list of eigenvalues (and eigenvectors) is exhaustive because $\dim \left(\mathbb{F}^n \right)=n$.
        \item Let $U \subseteq \mathbb{F}^n$ be an invariant subspace under $T$.
		Take any $u=\sum^{n}_{i=1} \alpha_i e_i \in U$ and suppose $\alpha_k \neq 0$ for some $k$.
		By Lagrange interpolation, there exists a polynomial $p$ such that $p(i)=\delta_{i,k}$ for all $i \in \{1, \dots, n\}$.
		Since $U$ is invariant under $T$, it is also invariant under $p(T)$, and so
        \[p(T)u=\sum^{n}_{i=1} \alpha_i p(T) e_i=\sum^{n}_{i=1} \alpha_i p(i) e_i=\alpha_k e_k \in U \implies e_k \in U.\]
        Repeating this argument for every index with a nonzero coefficient in some element of $U$ shows that $U$ contains each of the basis vectors $e_1$, $\dots$, $e_n$.
		Hence, $U=\operatorname{span} \{e_i: i \in S\}$ for some $S \subseteq \{1, \dots, n\}$.

        Conversely, any such span is invariant because $Te_i=ie_i$ belongs to that span.
		There are $2^n$ such subspaces, and they exhaust all invariant subspaces of $T$. \qh
    \end{subexercises}
\end{csp}

\begin{apex}[5a43]
    Suppose that $V$ is finite-dimensional, $\dim V > 1$, and $T \in \lin{V}$.
	Prove that $\set{p(T) \mid p \in \pcal(\fbb)} \neq \lin{V}$.
\end{apex}

\begin{me}
	Let $v_1, \ldots, v_n$ be a basis for $V$, with $n = \dim V$.
	Consider the operators $T_1, T_2 \in \lin V$ defined by
    \[T_1v_1 = v_2, \quad T_1v_i = 0~\text{for}~i = 2, \ldots, n,\]
    and
    \[T_2v_1 = v_1, \quad T_2v_i = 0~\text{for}~i = 2, \ldots, n.\]
    Then $T_2T_1v_1 = T_2(T_1v_1) = T_2v_2 = 0$, and $T_1T_2v_1 = T_1(T_2v_1) = T_1v_1 = v_2$.
	Hence, $T_2T_1 \neq T_1T_2$, so $T_1$ and $T_2$ do not commute.
	Let $S = \set{p(T) \mid p \in \pcal(\fbb)}$. Let $p, q \in \pcal$ be defined as
    \[p(z) = a_0 + a_1 z + \dots + a_m z^m, \quad q(z) = b_0 + b_1 z + \dots + b_k z^k.\]
    Since $p(T)q(T) = q(T)p(T)$, it follows that all operators in $S$ commute.
    However, if $T_1 = r(T)$ and $T_2 = s(T)$ for some polynomials $r, s \in \pcal$, then $T_1$ and $T_2$ would commute, which is a contradiction.
    Hence, $T_1$ and $T_2$ cannot both be in $S$, so $S \neq \lin{V}$.
\end{me}

\begin{apex}[5b29]
    Show that every operator on a finite-dimensional vector space of dimension at least two has an invariant subspace of dimension two.

    \note{\emph{\exref{5c6}} will give an improvement of this result when $\fbb = \cbb$.}
\end{apex}

\begin{csp}
    If $\mathbb{F}=\mathbb{C}$, the result is immediate: every operator on a finite-dimensional complex vector space has an upper-triangular matrix with respect to some basis $v_1$, $\dots$, $v_n$. Then $\operatorname{span}(v_1,v_2)$ is a $2$-dimensional invariant subspace. Hence, we restrict to $\mathbb{F}=\mathbb{R}$ from now on. \\

    Assume $\dim V \geq 2$ and let $T \in \mathcal{L}(V)$ have minimal polynomial $p$. Over $\mathbb{R}$, $p$ factors into linear and irreducible quadratic factors. \\

    \textbf{Case 1}: $p$ has an irreducible quadratic factor. Write $p(z)=(z^2+az+b)m(z)$. Pick $v \in V$ such that $x=m(T)v \neq 0$; then $(T^2+aT+bI)x=0$. Set $U=\operatorname{span}(x,Tx)$. Clearly, $T$ maps $U$ to itself since $T(Tx)=-bx-aTx \in U$. If $x$ and $Tx$ were linearly dependent, $x$ would be an eigenvector and its eigenvalue would be a real root of $z^2+az+b$, contradicting irreducibility. Hence $\dim U=2$. \\

    \textbf{Case 2}: $p$ splits completely into linear factors. Then $T$ is upper-triangularizable over $\mathbb{R}$. Let $v_1$, $\dots$, $v_n$ be a basis with respect to which the matrix of $T$ is upper-triangular. Then, $Tv_1 \in \operatorname{span}(v_1)$ and $Tv_2 \in \operatorname{span}(v_1, v_2)$. Therefore $\operatorname{span}(v_1,v_2)$ is a $2$-dimensional invariant subspace. \\

    These two cases cover all possibilities over $\mathbb{R}$, and so combining with trivial complex case finishes the proof.
\end{csp}

\begin{apex}[5c3]
    Suppose $T \in \lin{V}$ is invertible and $v_1, \ldots, v_n$ is a basis of $V$ with respect to which the matrix of $T$ is upper triangular, with $\lambda_1, \ldots, \lambda_n$ on the diagonal.
    Show that the matrix of $T\inv$ is also upper triangular with respect to the basis $v_1, \ldots, v_n$, with
    \[
        \frac{1}{\lambda_1}, \ldots, \frac{1}{\lambda_n}
    \]
    on the diagonal.
\end{apex}

\begin{me}
    Let $A$ be the matrix of $T$ with respect to the basis $v_1, \ldots, v_n$. 
    Since $T$ is invertible, $A$ is also invertible.
    Let $A = (a_{ij})$ be the upper-triangular matrix with $\lambda_1, \ldots, \lambda_n$ on the diagonal, and let $B = (b_{ij})$ be the matrix of $T\inv$ with respect to the same basis.
    Denote $b_j$ as the $j$-th column of $B$.
    Then we have
    \[
        Ab_j = e_j,
    \]
    where $e_j$ is the $j$-th column of the identity matrix. 
    In the $n$th row, we have $\lambda_n b_{nj} = \delta_{nj}$, hence $b_{nj} = 0$ for $j < n$ and $b_{nn} = \lambda_n\inv$.
    Now, consider the $(n-1)$-th row. We have
    \[
        a_{n-1,n-1}b_{n-1,j} + a_{n-1,n}b_{n,j} = \delta_{n-1,j}.
    \]
    For $j < n-1$, we have $b_{n,j} = 0$ and $\delta_{n-1,j} = 0$, so $b_{n-1,j} = 0$.
    For $j = n-1$, we have $b_{n,n-1} = 0$ and $\delta_{n-1,n-1} = 1$, so $b_{n-1,n-1} = a_{n-1,n-1}\inv = \lambda_{n-1}\inv$.
    Assume inductively that for some $k \in \{1, \ldots, n-1\}$, we have $b_{ij} = 0$ for all $i > j$ and $b_{ii} = \lambda_i\inv$ for all $i \geq k+1$.
    Now, consider the $k$-th row. We have
    \[
        a_{kk}b_{kj} + a_{k,k+1}b_{k+1,j} + \cdots + a_{kn}b_{nj} = \delta_{kj}.
    \]
    For $j < k$, we have $b_{ij} = 0$ for all $i > j \geq k$, so the left-hand side reduces to $a_{kk}b_{kj} = 0$, hence $b_{kj} = 0$.
    For $j = k$, we have $b_{ij} = 0$ for all $i > k$, so the left-hand side reduces to $a_{kk}b_{kk} = 1$, hence $b_{kk} = a_{kk}\inv = \lambda_k\inv$.
    By induction, we conclude that $B$ is upper-triangular with $\lambda_1\inv, \ldots, \lambda_n\inv$ on the diagonal.
\end{me}